### 2024-08-12 article.tex
Article debut

\documentclass[lettersize,journal]{IEEEtran}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{cite}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
% updated with editorial comments 8/9/2021

\begin{document}

\title{Neigbouring methods applied to telphonic base stations}

\end{document}

### 2024-08-13 article.tex
Ajout de la biblio
Avancement et ajout de glossaire

@@
 \documentclass[lettersize,journal]{IEEEtran}
+\usepackage[utf8]{inputenc}
 \usepackage{amsmath,amsfonts}
@@
 \usepackage{cite}
+\usepackage{booktabs}
+\usepackage[acronym]{glossaries}
+\usepackage[unicode=true,pdfusetitle,
+ bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
+ breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=true]
+ {hyperref}
+\hypersetup{
+ urlcolor=blue, linkcolor=black}
 \hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
-% updated with editorial comments 8/9/2021
+
+\global\long\def\BDsites{\textsf{BD\_sites}}
+
+\title{Adaptative neigbouring methods applied to telephonic base stations}
+\author{Paul MÉHAUD, Brendan SÉVELLEC}
+
+\makeglossaries
+
+\newacronym{arcep}{ARCEP}{French Regulatory Authority for Electronic Communications and Posts}
+\newacronym{anfr}{ANFR}{French National Frequency Agency}
 
 \begin{document}
+\maketitle
 
-\title{Neigbouring methods applied to telphonic base stations}
+\begin{abstract}
+  blabla
+\end{abstract}
+
+\section{Introduction}
+
+\section{Related works}
+
+\section{Databases}
+La base de données principale que nous allons utiliser est le résultat des recherches précédentes de Delphine PAQUIRY.
+En effet, l'année dernière une partie de son stage
+
+\subsection{Main database}
+
+\cite{main_database}
+
+\begin{table}[!b]
+    \centering
+    \caption{Description of the dataset}
+    \label{data_columns}
+    \begin{tabular}{ll}
+        \toprule
+        \textbf{Column} & \textbf{Description} \\
+        \cmidrule(lr){1-2}
+        \textsl{BS\_anfr\_id} & \acrshort{anfr} base station ID \\ 
+        \textsl{x, y, latitude, longitude} & Base station coordinates \\ 
+        \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
+        \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the base station \\ 
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+On portera surtout notre attention sur les champs suivants :
+\begin{enumerate}
+    \item \textsl{longitude}, \textsl{latitude} : coordonnées de chaque site;
+    \item \textsl{nom\_op} : nom commercial de l'opérateur;
+    \item \textsl{nom\_reg}, \textsl{nom\_dep} et \textsl{nom\_com} : nom de la région, du département et de la commune d'implantation du site;
+    \item \textsl{site\_$x$g} : équipement du site en technologie $x$G ($x\in\{ 2,\dots,5\}$);
+    \item \textsl{num\_site} : identifiant du site issu du SI de l'opérateur. 
+\end{enumerate}
+
+\section{Finding potential neighbours}
+\noindent When we are looking for neighbours, we need, at first, a list of potential neighbours for each base stations.
+Here are the different methods we can use to solve this problem:
+
+\subsection{Delaunay triangulation}
+\noindent The Delaunay triangulation is named after Boris DELAUNAY for his work on it from 1934 [citer l'article].
+
+The principle of this method is quite simple. Let $P$ be a set of points in the plane and $D(P)$ the triangulation we are looking for.
+A triangle $t_i$ is in $D(P)$ if its circumcircle does not contain any point inside (it can contain points on the border).
+
+However, a Delaunay triangulation is not unique.
+
+You can find an illustration of this method in figure \ref{del_tri}.
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{images/illus_graphs/Delaunay_circumcircles_vectorial.svg.png}
+    \caption{Example of a Delaunay triangulation}
+    \label{del_tri}
+\end{figure}
+
+\subsection{Gabriel graph}
+\noindent The Gabriel graph is a subgraph of a Delaunay triangulation. Thus, if the Delaunay triangulation is given, it can be found in a linear time.
+
+Gabriel graphs are named after K. Ruben Gabriel, who introduced them in a paper with Robert R. Sokal in 1969[citer].
+
+The principle is really close to the one presented before. Let $G$
+
+\subsection{$k$-NN graph}
+
+\section{Results}
+
+\section{Conclusion}
+
+[Ouverture : prendre en compte les zazimuths]
+
+\printglossary[type=\acronymtype]
+
+\bibliographystyle{alpha}
+\bibliography{./biblio.bib}
 

### 2024-08-13 article.tex
adding abstract + intro + start of data

@@
 \begin{abstract}
-  blabla
+  The field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\%
+  in 2023 in the world, and 97\% in France. Therefore, the collected datas represent a big opportunity for telecommunication
+  companies to predict their customers behaviour for internal or marketing purposes. Thus, it is primordial for these companies
+  to be able to determinate if a user is moving. For that, it is necessary to understand the neighbouring relationships between the 
+  telephonic base stations. This article aims at comparing different method, ellaborated in order to adaptively detect these
+  relationship between telephonic base stations given their geographical positions.
 \end{abstract}
@@
 \section{Introduction}
+    \IEEEPARstart{T}{his} article is the continuation of the work done by Delphine Paquiry in this paper \cite{art_del_paq}.
+    It aims at discovering the neighbouring relationships between base stations from their geographical positions, using a 
+    measure of the density of base station.
 
+    For that, it is necessary to describe and analyse the databases that have been used during the research, then to present 
+    the different appoaches that always consist of these steps : establish a first neighbouring graph, compute the base station 
+    densities and filter this graph with different criteria using this information. The final step is to present the results
+    of the different approches and conclude.
 \section{Related works}
@@
 \section{Databases}
-La base de données principale que nous allons utiliser est le résultat des recherches précédentes de Delphine PAQUIRY.
-En effet, l'année dernière une partie de son stage
+    Several databases have been used in order to test the different aspects of the methods. However, one of
+    them is directly necessary to the method itself.
 
@@
 
-\cite{main_database}
+    This database \cite{main_database} contains all the information needed to the application of the method. It is from
+    \acrfull{arcep}, which is a french national organisation that
+
+    The fields that are being used here are the following :
 
@@
     \end{table}
-
-On portera surtout notre attention sur les champs suivants :
-\begin{enumerate}
-    \item \textsl{longitude}, \textsl{latitude} : coordonnées de chaque site;
-    \item \textsl{nom\_op} : nom commercial de l'opérateur;
-    \item \textsl{nom\_reg}, \textsl{nom\_dep} et \textsl{nom\_com} : nom de la région, du département et de la commune d'implantation du site;
-    \item \textsl{site\_$x$g} : équipement du site en technologie $x$G ($x\in\{ 2,\dots,5\}$);
-    \item \textsl{num\_site} : identifiant du site issu du SI de l'opérateur. 
-\end{enumerate}
 

### 2024-08-14 article.tex
Graphs et critères expliqués

--- 2024-08-13 article.tex
@@
-\documentclass[lettersize,journal]{IEEEtran}
+\documentclass[lettersize,journal,english]{IEEEtran}
+\usepackage[T1]{fontenc}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{booktabs}
+\usepackage{units}
 \usepackage[acronym]{glossaries}
@@
 \newacronym{anfr}{ANFR}{French National Frequency Agency}
+\newacronym{bs}{BS}{Base Station}
+
+\usepackage[english,french]{babel}
 
 \begin{document}
+\selectlanguage{english}
 \maketitle
@@
         \cmidrule(lr){1-2}
-        \textsl{BS\_anfr\_id} & \acrshort{anfr} base station ID \\ 
+        \textsl{BS\_anfr\_id} & \acrshort{anfr} \acrshort{bs} ID \\ 
         \textsl{x, y, latitude, longitude} & Base station coordinates \\ 
         \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
-        \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the base station \\ 
+        \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the \acrshort{bs} \\ 
         \bottomrule
@@
 \section{Finding potential neighbours}
-\noindent When we are looking for neighbours, we need, at first, a list of potential neighbours for each base stations.
+\noindent When we are looking for neighbours, we need, at first, a list of potential neighbours for each \acrfull{bs}.
 Here are the different methods we can use to solve this problem:
@@
 
-The principle is really close to the one presented before. Let $G$
+Formally, it is the graph $G$ with vertex set $S$ in which any two distinct points $p\in S$ and $q\in S$ are adjacent precisely when the closed disc having pq as a diameter contains no other points.
 
 \subsection{$k$-NN graph}
+\noindent Nevertheless, the two methods presented above are triangulation, that is to say that they do not connect each \acrshort{bs} to all of its potential neighbours.
+
+One simple idea to get rid of this problem could be solved by connecting each \acrshort{bs} to its $k$ nearest neighbours.
+
+\section{Finding the real neighbours}
+
+\noindent Each of the precedent methods gives us a list of potential neighbours for each \acrshort{bs}. However, we know that some of this neighbouring connexions are wrong,
+because some \acrshort{bs} will be \og hidden\fg{} by others.
+
+Thus, we need to find methods to suppress bad connexions. That was made by Delphine.
+
+The main innovation of our work is to take in account the difference of \acrshort{bs}'s density.
+
+\subsection{Measurement of \acrshort{bs} density}
+\noindent To simplify the explanation, and because it is related, we will assume that solving this problem is equivalent to finding the \acrshort{bs} situated in \og cities\fg{}.
+
+\subsubsection{DBScan}
+
+\subsubsection{HDBScan}
+
+\subsubsection{$3$-NN mean distance}
+One provider $\gamma$
+
+To classify each base station we need a method. Here, we will take the mean distance to the 3 nearest neighbours.
+
+Let's call this value $\gamma$, in $\unit{km}$. So, we have 4 different categories.
+For each category, we will apply a different distance and angle criterion :
+
+\subsection{Filtering criteria}
+
+\begin{table}[!b]
+    \centering
+    \caption{Summary of criteria values}
+    \label{crit_summary}
+    \begin{tabular}{clcc}
+        \toprule
+        \textbf{$\gamma$} & \textbf{Description} & \textbf{max\_distance} & \textbf{min\_angle} \\
+        \cmidrule(lr){1-4}
+        $\left[0, 1\right]$ & city center & $\unit[2]{km}$ & $5^\circ$ \\
+        $\left]1, 2\right]$ & urban area & $\unit[5]{km}$ & $10^\circ$ \\
+        $\left]2, 4\right]$ & extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
+        $\left]4, \infty\right[$ & courntryside & $\unit[15]{km}$ & $20^\circ$ \\
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{images/illus_crit/points.png}
+    \caption{Example of a Delaunay triangulation}
+    \label{crit_pts}
+\end{figure}
+
+\begin{figure}[!b]
+    \centering
+    \includegraphics[width=2.5in]{images/illus_crit/distance_elim.png}
+    \caption{Example of a Delaunay triangulation}
+    \label{crit_dis}
+\end{figure}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{images/illus_crit/angle_elim.png}
+    \caption{Example of a Delaunay triangulation}
+    \label{crit_ang}
+\end{figure}
+
+\begin{figure}[!b]
+    \centering
+    \includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}
+    \caption{Example of a Delaunay triangulation}
+    \label{crit_qua}
+\end{figure}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=2.5in]{images/illus_crit/neighs.png}
+    \caption{Example of a Delaunay triangulation}
+    \label{crit_nei}
+\end{figure}
+
+\subsubsection{Distance criterion}
+Each \acrshort{bs} has its proper coverage area, which is not infinite. As a matter of fact, we need to suppress longer edges.
+
+\subsubsection{Angle criterion}
+For each \acrshort{bs}, we
+
+\subsubsection{Quadrant criterion}
 

### 2024-08-14 article.tex

@@
 \end{table}
-
-On portera surtout notre attention sur les champs suivants :
-\begin{enumerate}
-    \item \textsl{longitude}, \textsl{latitude} : coordonnées de chaque site;
-    \item \textsl{nom\_op} : nom commercial de l'opérateur;
-    \item \textsl{nom\_reg}, \textsl{nom\_dep} et \textsl{nom\_com} : nom de la région, du département et de la commune d'implantation du site;
-    \item \textsl{site\_$x$g} : équipement du site en technologie $x$G ($x\in\{ 2,\dots,5\}$);
-    \item \textsl{num\_site} : identifiant du site issu du SI de l'opérateur. 
-\end{enumerate}
 

### 2024-08-14 article.tex
Ajout d'un glossaire

@@
 \usepackage{units}
-\usepackage[acronym]{glossaries}
 \usepackage[unicode=true,pdfusetitle,
  bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
- breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=true]
- {hyperref}
+ breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=true]{hyperref}
 \hypersetup{
  urlcolor=blue, linkcolor=black}
+\usepackage[acronym]{glossaries}
 \hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
@@
 
+\setglossarypreamble{All definitions are from \href{https://www.dictionary.com/}{Dictionnary.com}}
+
+\newglossaryentry{base station}
+{
+    name=base station,
+    description={A fixed transmitter that forms part of an otherwise mobile radio network}
+}
+
 \newacronym{arcep}{ARCEP}{French Regulatory Authority for Electronic Communications and Posts}
 \newacronym{anfr}{ANFR}{French National Frequency Agency}
-\newacronym{bs}{BS}{Base Station}
+\newacronym{bs}{BS}{\Gls{base station}}
 
@@
 \printglossary[type=\acronymtype]
+\printglossary
 

### 2024-08-14 article.tex
Delaunay detailing

--- 2024-08-14 article.tex
@@
 \usepackage[utf8]{inputenc}
-\usepackage{amsmath,amsfonts}
+\usepackage{amsmath,amsfonts,amssymb}
 \usepackage{algorithmic}
@@
     For that, it is necessary to describe and analyse the databases that have been used during the research, then to present 
-    the different appoaches that always consist of these steps : establish a first neighbouring graph, compute the base station 
+    the different approaches that always consist of these steps : establish a first neighbouring graph, compute the base station 
     densities and filter this graph with different criteria using this information. The final step is to present the results
-    of the different approches and conclude.
+    of the different approaches and conclude.
 \section{Related works}
@@
 
-    The fields that are being used here are the following :
+    The fields that are being used here are described in Table~\ref{data_columns}
 
@@
 
-The principle of this method is quite simple. Let $P$ be a set of points in the plane and $D(P)$ the triangulation we are looking for.
-A triangle $t_i$ is in $D(P)$ if its circumcircle does not contain any point inside (it can contain points on the border).
+A Delaunay triangulation of a set of points in the plane subdivides their convex hull into triangles whose circumcircles 
+do not contain any of the points. You can find an illustration of this method in Figure~\ref{del_tri}.
+A Delaunay triangulation is not unique if there exists 4 concyclic points.
 
-However, a Delaunay triangulation is not unique.
+It can be associated with an unoriented graph $G = (P, U)$ where $U$ is composed of every edge of $D(P)$.
+Therefore, it is often used as a method to detect the closest neighbors \cite{delaunay_neighbor} (each nodes that are considered neighbors are
+connected by an edge in G).
 
-You can find an illustration of this method in figure \ref{del_tri}.
 \begin{figure}[!t]

### 2024-08-14 article.tex
Ajout city detection et angle crit

--- 2024-08-14 article.tex
@@
 \newacronym{bs}{BS}{\Gls{base station}}
+\newacronym{dbscan}{DBScan}{Density-Based Spatial Clustering of Applications with Noise}
+\newacronym{hdbscan}{HDBScan}{Hierarchical Density-Based Spatial Clustering of Applications with Noise}
 
@@
 
-You can find an illustration of this method in figure \ref{del_tri}.
+You can find an illustration of this method in Figure~\ref{del_tri}.
 \begin{figure}[!t]
@@
 
-\subsubsection{DBScan}
+\subsubsection{\acrshort{dbscan}}
+When thinking of density-based clustering, one of the first methods that comes in mind is probably \acrshort{dbscan}.
+It is really powerful because we only have two parameters to modify.
 
-\subsubsection{HDBScan}
+Despite the efficiency of this method, it is not the best adapted to our problem because it's only giving us if a \acrshort{bs} is considered in a city or not.
+We wanted a more continuous method.
+
+\subsubsection{\acrshort{hdbscan}}
 
 \subsubsection{$3$-NN mean distance}
-One provider $\gamma$
+To classify each base station we need a method.
 
-To classify each base station we need a method. Here, we will take the mean distance to the 3 nearest neighbours.
+For each base station the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma$, in $\unit{km}$), thus making it possible to classify each base station into four different categories listed in Table~\ref{crit_summary}.
 
-Let's call this value $\gamma$, in $\unit{km}$. So, we have 4 different categories.
-For each category, we will apply a different distance and angle criterion :
+To make this method working properly, only \acrshort{bs} from one provider have to be kept into the calculation process.
+Moreover, this values are working well on France but it is not proven that it can work in another country. If someone uses this methods, values could be modified.
 
@@
 \subsubsection{Angle criterion}
-For each \acrshort{bs}, we
+For each \acrshort{bs}, a potential neighbour can be \og hidden\fg{} by another one which nearer because there is a too narrow angle between those two \acrshort{bs}.
+This criterion, will therefore suppress the longest edge between two \acrshort{bs} separated by a too small angle. This is illustrated in Figure \ref{crit_ang}.
 

### 2024-08-14 article.tex

@@
 
-The principle of this method is quite simple. Let $P$ be a set of points in the plane and $D(P)$ the triangulation we are looking for.
-A triangle $t_i$ is in $D(P)$ if its circumcircle does not contain any point inside (it can contain points on the border).
+A Delaunay triangulation of a set of points in the plane subdivides their convex hull into triangles whose circumcircles 
+do not contain any of the points. You can find an illustration of this method in Figure~\ref{del_tri}.
 
-However, a Delaunay triangulation is not unique.
+It can be associated with an unoriented graph $G = (P, U)$ where $U$ is composed of every edge of $D(P)$.
+Therefore, it is often used as a method to detect the closest neighbors \cite{delaunay_neighbor} (each nodes that are considered neighbors are
+connected by an edge in $G$).
 
-You can find an illustration of this method in Figure~\ref{del_tri}.
 \begin{figure}[!t]

### 2024-08-14 article.tex
Modification biblio style et ajout d'un mot au glossaire

@@
     description={A fixed transmitter that forms part of an otherwise mobile radio network}
+}
+
+\newglossaryentry{convHull}
+{
+    name=convex hull,
+    description={The smallest convex set containing a given set}
 }
@@
 
-A Delaunay triangulation of a set of points in the plane subdivides their convex hull into triangles whose circumcircles 
+A Delaunay triangulation of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles 
 do not contain any of the points. You can find an illustration of this method in Figure~\ref{del_tri}.
@@
 
-\bibliographystyle{alpha}
+\bibliographystyle{IEEEtran}
 \bibliography{./biblio.bib}

### 2024-08-14 article.tex
changement d'une variable

@@
 
-For each base station the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma$, in $\unit{km}$), thus making it possible to classify each base station into four different categories listed in Table~\ref{crit_summary}.
+For each base station the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in $\unit{km}$), thus making it possible to classify each base station into four different categories listed in Table~\ref{crit_summary}.
 
@@
         \toprule
-        \textbf{$\gamma$} & \textbf{Description} & \textbf{max\_distance} & \textbf{min\_angle} \\
+        \textbf{$\gamma_i$} & \textbf{Description} & \textbf{max\_distance} & \textbf{min\_angle} \\
         \cmidrule(lr){1-4}

### 2024-08-14 article.tex
pres arcep finie
Ajout des références delaunay et gabriel

@@
     This database \cite{main_database} contains all the information needed to the application of the method. It is from
-    \acrfull{arcep}, which is a french national organisation that
+    \acrfull{arcep}, which is an independent French administrative authority responsible for regulating electronic and postal communications and press distribution.
 
-    The fields that are being used here are described in Table~\ref{data_columns}
+    The fields that are being used here are described in Table~\ref{data_columns}.
 
@@
 \subsection{Delaunay triangulation}
-\noindent The Delaunay triangulation is named after Boris DELAUNAY for his work on it from 1934 [citer l'article].
+\noindent The Delaunay triangulation is named after Boris DELAUNAY for his work on it from 1934 \cite{art_delaunay}.
 
@@
 
-Gabriel graphs are named after K. Ruben Gabriel, who introduced them in a paper with Robert R. Sokal in 1969[citer].
+Gabriel graphs are named after K. Ruben Gabriel, who introduced them in a paper with Robert R. Sokal in 1969 \cite{art_gabriel}.
 

### 2024-08-14 article.tex
Changing potential neighbours organisation

--- 2024-08-14 article.tex
@@
     description={A fixed transmitter that forms part of an otherwise mobile radio network}
-}
-
-\newglossaryentry{convHull}
-{
-    name=convex hull,
-    description={The smallest convex set containing a given set}
 }
@@
 \noindent When we are looking for neighbours, we need, at first, a list of potential neighbours for each \acrfull{bs}.
-Here are the different methods we can use to solve this problem:
+For that, we will construct a neigbouring graph $G = (P, U)$ (each base station that are considered neighbors are
+connected by an edge) where $P$ is the set of all base stations. 
+Here are the different methods we can build this graph with:
+
+\subsection{$k$-NN graph}
+\noindent The most intuitive method is to connect each \acrshort{bs} to its $k$ nearest neighbours, where $k \in \mathbb{N}^*$ 
+is a parameter to be fixed.
+
+However, this method can be criticized, because it always finds $k$ neighbor to each base stations, no matter the reality of the 
+data.
 
@@
 
-A Delaunay triangulation of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles 
+A Delaunay triangulation of a set of points in the plane subdivides their convex hull into triangles whose circumcircles 
 do not contain any of the points. You can find an illustration of this method in Figure~\ref{del_tri}.
 
-It can be associated with an unoriented graph $G = (P, U)$ where $U$ is composed of every edge of $D(P)$.
-Therefore, it is often used as a method to detect the closest neighbors \cite{delaunay_neighbor} (each nodes that are considered neighbors are
-connected by an edge in $G$).
+A Voronoi diagram is a tessellation pattern in which $n$ points scattered on a plane subdivides in 
+exactly $n$ cells enclosing a portion of the plane that is closest to each point.
+
+The Delaunay triangulation is the pendant of the Voronoi diagram in the sense that two points are connected in the
+Delaunay triangulation if their associated cells share an edge in the Voronoi diagram.
+
+Therefore, another approach, consists in computing a Delaunay triangulation and build a neighouring graph $G = (P, U)$ where $U$ 
+is composed of every edge of $D(P)$. Which is equivalent to consider two base station as potential neighbors if their associated
+cells are touching each other in the Voronoi diagram.
+
+This method has already been used in articles in the past \cite{delaunay_neighbor}.
 
@@
 
-Formally, it is the graph $G$ with vertex set $S$ in which any two distinct points $p\in S$ and $q\in S$ are adjacent precisely when the closed disc having pq as a diameter contains no other points.
-
-\subsection{$k$-NN graph}
-\noindent Nevertheless, the two methods presented above are triangulation, that is to say that they do not connect each \acrshort{bs} to all of its potential neighbours.
-
-One simple idea to get rid of this problem could be solved by connecting each \acrshort{bs} to its $k$ nearest neighbours.
+Formally, it is the graph $G = (P, U)$ in which any two distinct points $p, q \in P$ are adjacent precisely when the closed disc having $pq$ as a diameter contains no other points.
 
@@
 
-\bibliographystyle{IEEEtran}
+\bibliographystyle{alpha}
 \bibliography{./biblio.bib}

### 2024-08-14 article.tex

@@
 \subsection{Delaunay triangulation}
-\noindent The Delaunay triangulation is named after Boris DELAUNAY for his work on it from 1934 [citer l'article].
+\noindent The Delaunay triangulation is named after Boris DELAUNAY for his work on it from 1934 \cite{art_delaunay}.
 
-A Delaunay triangulation of a set of points in the plane subdivides their convex hull into triangles whose circumcircles 
+A Delaunay triangulation of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles 
 do not contain any of the points. You can find an illustration of this method in Figure~\ref{del_tri}.

### 2024-08-14 article.tex
Ajout explication interet gabriel
Ajout d'une illustration de voronoi

@@
     \centering
-    \includegraphics[width=2.5in]{images/illus_graphs/Delaunay_circumcircles_vectorial.svg.png}
-    \caption{Example of a Delaunay triangulation}
+    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_circumcircles_vectorial.png}}
+    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_Voronoi.png}}
+    \caption{Example of a Delaunay triangulation (in black) and Voronoi tessellation (in red)}
     \label{del_tri}
@@
 Formally, it is the graph $G = (P, U)$ in which any two distinct points $p, q \in P$ are adjacent precisely when the closed disc having $pq$ as a diameter contains no other points.
+
+Basically, the interset of this method, compared to the Delaunay triangulation, is that it is adding a first level of filtration for bad neighbouring connexions.
 

### 2024-08-14 article.tex
minor modifications

--- 2024-08-14 article.tex
@@
 
+Basically, the interset of this method, compared to the Delaunay triangulation, is that it is adding a first level of filtration for bad neighbouring connexions.
+
 \section{Finding the real neighbours}
@@
 \noindent Each of the precedent methods gives us a list of potential neighbours for each \acrshort{bs}. However, we know that some of this neighbouring connexions are wrong,
-because some \acrshort{bs} will be \og hidden\fg{} by others.
+either because of the neighboring graph construction method or physical specificities linked to the base stations themselves.
 
-Thus, we need to find methods to suppress bad connexions. That was made by Delphine.
+Thus, we need to find methods to detetect and erase these bad connexions.
 
-The main innovation of our work is to take in account the difference of \acrshort{bs}'s density.
+The main innovation of our work compared to this one \cite{art_del_paq} is to take in account the difference of \acrshort{bs}'s density.
 

### 2024-08-14 article.tex
Modification des labels

--- 2024-08-14 article.tex
@@
 
-    The fields that are being used here are described in Table~\ref{data_columns}.
+    The fields that are being used here are described in Table~\ref{table:data_columns}.
 
@@
     \caption{Description of the dataset}
-    \label{data_columns}
+    \label{table:data_columns}
     \begin{tabular}{ll}
@@
 A Delaunay triangulation of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles 
-do not contain any of the points. You can find an illustration of this method in Figure~\ref{del_tri}.
+do not contain any of the points. You can find an illustration of this method in Figure~\ref{fig:del_tri}.
 
@@
     \caption{Example of a Delaunay triangulation (in black) and Voronoi tessellation (in red)}
-    \label{del_tri}
+    \label{fig:del_tri}
 \end{figure}
@@
 
-For each base station the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in $\unit{km}$), thus making it possible to classify each base station into four different categories listed in Table~\ref{crit_summary}.
+For each base station the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in $\unit{km}$), thus making it possible to classify each base station into four different categories listed in Table~\ref{table:crit_summary}.
 
@@
     \caption{Summary of criteria values}
-    \label{crit_summary}
+    \label{table:crit_summary}
     \begin{tabular}{clcc}
@@
     \caption{Example of a Delaunay triangulation}
-    \label{crit_pts}
+    \label{table:crit_pts}
 \end{figure}
@@
     \caption{Example of a Delaunay triangulation}
-    \label{crit_dis}
+    \label{table:crit_dis}
 \end{figure}
@@
     \caption{Example of a Delaunay triangulation}
-    \label{crit_ang}
+    \label{table:crit_ang}
 \end{figure}
@@
     \caption{Example of a Delaunay triangulation}
-    \label{crit_qua}
+    \label{table:crit_qua}
 \end{figure}
@@
     \caption{Example of a Delaunay triangulation}
-    \label{crit_nei}
+    \label{table:crit_nei}
 \end{figure}
@@
 For each \acrshort{bs}, a potential neighbour can be \og hidden\fg{} by another one which nearer because there is a too narrow angle between those two \acrshort{bs}.
-This criterion, will therefore suppress the longest edge between two \acrshort{bs} separated by a too small angle. This is illustrated in Figure \ref{crit_ang}.
+This criterion, will therefore suppress the longest edge between two \acrshort{bs} separated by a too small angle. This is illustrated in Figure \ref{table:crit_ang}.
 

### 2024-08-14 article.tex
Mise en boite des illustrations

@@
     \centering
-    \includegraphics[width=2.5in]{images/illus_crit/points.png}
+    \boxed{\includegraphics[width=2.5in]{images/illus_crit/points.png}}
     \caption{Example of a Delaunay triangulation}
@@
     \centering
-    \includegraphics[width=2.5in]{images/illus_crit/distance_elim.png}
+    \boxed{\includegraphics[width=2.5in]{images/illus_crit/distance_elim.png}}
     \caption{Example of a Delaunay triangulation}
@@
     \centering
-    \includegraphics[width=2.5in]{images/illus_crit/angle_elim.png}
+    \boxed{\includegraphics[width=2.5in]{images/illus_crit/angle_elim.png}}
     \caption{Example of a Delaunay triangulation}
@@
     \centering
-    \includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}
+    \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
     \caption{Example of a Delaunay triangulation}
@@
     \centering
-    \includegraphics[width=2.5in]{images/illus_crit/neighs.png}
+    \boxed{\includegraphics[width=2.5in]{images/illus_crit/neighs.png}}
     \caption{Example of a Delaunay triangulation}

### 2024-08-15 article.tex
Image cropping + amelioration prez crit + ...

@@
 
-Basically, the interset of this method, compared to the Delaunay triangulation, is that it is adding a first level of filtration for bad neighbouring connexions.
+Basically, the interset of this method, compared to the Delaunay triangulation, is that it is adding a first level of filtration to suppress some neighbouring connexions.
 
@@
         \toprule
-        \textbf{$\gamma_i$} & \textbf{Description} & \textbf{max\_distance} & \textbf{min\_angle} \\
+        \textbf{$\gamma_i$} & \textbf{Description} & \textbf{\emph{max\_distance}} & \textbf{\emph{min\_angle}} \\
         \cmidrule(lr){1-4}
@@
     \caption{Example of a Delaunay triangulation}
-    \label{table:crit_pts}
+    \label{fig:crit_pts}
 \end{figure}
@@
     \caption{Example of a Delaunay triangulation}
-    \label{table:crit_dis}
+    \label{fig:crit_dis}
 \end{figure}
@@
     \caption{Example of a Delaunay triangulation}
-    \label{table:crit_ang}
+    \label{fig:crit_ang}
 \end{figure}
@@
     \caption{Example of a Delaunay triangulation}
-    \label{table:crit_qua}
+    \label{fig:crit_qua}
 \end{figure}
@@
     \caption{Example of a Delaunay triangulation}
-    \label{table:crit_nei}
+    \label{fig:crit_nei}
 \end{figure}
@@
 \subsubsection{Distance criterion}
-Each \acrshort{bs} has its proper coverage area, which is not infinite. As a matter of fact, we need to suppress longer edges.
+When looking at the results of Delaunay triangulation, we realise that some edges, mostly on the border of $P$ are too long. Indeed, a \acrshort{bs} does not have an infinite coverage area.
+
+As a consequence, for each \acrshort{bs} the neighbouring connexions that are longer than a certain value, called \emph{max\_distance}, are suppressed (cf. Table~\ref{table:crit_summary}).
 
@@
 For each \acrshort{bs}, a potential neighbour can be \og hidden\fg{} by another one which nearer because there is a too narrow angle between those two \acrshort{bs}.
-This criterion, will therefore suppress the longest edge between two \acrshort{bs} separated by a too small angle. This is illustrated in Figure \ref{table:crit_ang}.
+This criterion, will therefore suppress the longest edge between two \acrshort{bs} separated by a too small angle. This is illustrated in Figure~\ref{fig:crit_ang}.
 
@@
 \section{Results}
+
+\subsection{Combining criteria}
+As a matter of optimisation, criteria are applied one after another. For example, the base graph is Delaunay triangulation and we apply distance then angle.
+The principle is that angle criterion will be applied on the Delaunay graph filtered with the distance criterion.
+
+As a consequence, results differ according to the order in which the criteria are applied.
+
+The best is Delaunay with distance and then angle.
 

### 2024-08-15 article.tex
Calrification angle et modification détection des villes

@@
     \subsection{Main database}
-
     This database \cite{main_database} contains all the information needed to the application of the method. It is from
@@
 \section{Finding the real neighbours}
-
 \noindent Each of the precedent methods gives us a list of potential neighbours for each \acrshort{bs}. However, we know that some of this neighbouring connexions are wrong,
@@
 \subsection{Measurement of \acrshort{bs} density}
-\noindent To simplify the explanation, and because it is related, we will assume that solving this problem is equivalent to finding the \acrshort{bs} situated in \og cities\fg{}.
+\noindent To make it easier to understand, and because it is related,
+we will assume that solving this problem is equivalent to finding the \acrshort{bs} situated in \og cities\fg{}.
+
+Moreover, to simplify the problem, each \acrshort{bs} will be classified in one of this four categories :
+\begin{itemize}
+    \item \emph{city center};
+    \item \emph{urban area};
+    \item \emph{extra-urban area};
+    \item \emph{courntryside}.
+\end{itemize}
 
@@
     \label{table:crit_summary}
-    \begin{tabular}{clcc}
+    \begin{tabular}{lcc}
         \toprule
-        \textbf{$\gamma_i$} & \textbf{Description} & \textbf{\emph{max\_distance}} & \textbf{\emph{min\_angle}} \\
-        \cmidrule(lr){1-4}
-        $\left[0, 1\right]$ & city center & $\unit[2]{km}$ & $5^\circ$ \\
-        $\left]1, 2\right]$ & urban area & $\unit[5]{km}$ & $10^\circ$ \\
-        $\left]2, 4\right]$ & extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
-        $\left]4, \infty\right[$ & courntryside & $\unit[15]{km}$ & $20^\circ$ \\
+        \textbf{Description} & \textbf{\emph{max\_distance}} & \textbf{\emph{min\_angle}} \\
+        \cmidrule(lr){1-3}
+        city center & $\unit[2]{km}$ & $5^\circ$ \\
+        urban area & $\unit[5]{km}$ & $10^\circ$ \\
+        extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
+        courntryside & $\unit[15]{km}$ & $20^\circ$ \\
         \bottomrule
@@
 \subsubsection{Distance criterion}
-When looking at the results of Delaunay triangulation, we realise that some edges, mostly on the border of $P$ are too long. Indeed, a \acrshort{bs} does not have an infinite coverage area.
+When looking at the results of Delaunay triangulation, we realise that some edges, mostly on the border of $P$ are too long.
 
-As a consequence, for each \acrshort{bs} the neighbouring connexions that are longer than a certain value, called \emph{max\_distance}, are suppressed (cf. Table~\ref{table:crit_summary}).
+Indeed, a \acrshort{bs} does not have an infinite coverage area.
+As a consequence, for each \acrshort{bs} the neighbouring connexions that are longer than a certain value, called \emph{max\_distance} (cf.
+Table~\ref{table:crit_summary}), are suppressed.
 
 \subsubsection{Angle criterion}
-For each \acrshort{bs}, a potential neighbour can be \og hidden\fg{} by another one which nearer because there is a too narrow angle between those two \acrshort{bs}.
-This criterion, will therefore suppress the longest edge between two \acrshort{bs} separated by a too small angle. This is illustrated in Figure~\ref{fig:crit_ang}.
+Let $p$, $q$, $r$ be three \acrshort{bs} of $P$, where $q$ and $r$ are $p$'s potential neighbours.
+As said before, coverage areas of \acrshort{bs} are limited by physics, this also implies that $r$ can be \og hidden\fg{} from $p$ by $q$ because $q$ is between $p$ and $r$ [trouver qqch pour prouver ce que je dis].
+
+Therefore, the connexion between $p$ and $r$ needs to be suppressed.
+How?
+The angle $\widehat{qrp}$ is calculated and if it is narrower than a certain value, called \emph{min\_angle} (cf.
+Table~\ref{table:crit_summary}), the longest edge is suppressed.
 

### 2024-08-15 article.tex
quadrant criterion explanations

--- 2024-08-15 article.tex
@@
 
-Gabriel graphs are named after K. Ruben Gabriel, who introduced them in a paper with Robert R. Sokal in 1969 \cite{art_gabriel}.
+Gabriel graphs are named after K. Ruben Gabriel, who introduced them in a paper with Robert R. Sokal in 1969 \cite{10.2307/2412323}.
 
@@
 \subsubsection{Quadrant criterion}
+A version of this criterion, that was introduced here \cite{10201211} and used here \cite{art_del_paq}. Its goal is
+to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the 
+$k$-NN potential neigbours method.
+
+It consists in dividing the space around each base station into quadrants and keeping only a certain number of potential neighbours
+in each of the quadrants. The number of quadrants has been fixed to 6 (optimized here \cite{art_del_paq}).
+
+The criterion has been upgraded by adding the possibility to rotate the quadrants. The offset angle selected, which is between 0 and 
+60 degrees, is the one that maximises the sum of the distances of the potential neighbours to their closest quadrant delimitation.
+
+In other words, it tends to select the angle with which the potential neighbors are as much in the middle of their respective quadrants
+as possible.
+
+The quadrant criterion is illustrated here Fig~\ref{fig:crit_qua}
 

### 2024-08-16 article.tex
grammar correction
Ajout d'infos sur la database

--- 2024-08-15 article.tex
@@
 
+    \begin{table}[!t]
+        \centering
+        \caption{Summary of technologies}
+        \label{table:techno_numbers}
+        \begin{tabular}{cccccc}
+            \toprule
+            \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
+            \cmidrule(lr){1-6}
+            \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
+            \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
+            \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
+            \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
+            \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
+            \bottomrule
+        \end{tabular}
+    \end{table}
+
 \begin{table}[!b]
@@
 \subsubsection{Quadrant criterion}
+A version of this criterion was introduced here \cite{10201211} and used here \cite{art_del_paq}. Its goal is
+to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the 
+$k$-NN potential neigbours method.
+
+It consists in dividing the space around each base station into quadrants and keeping only a certain number of potential neighbours
+in each of the quadrants. The number of quadrants has been fixed to 6 (optimized here \cite{art_del_paq}).
+
+The criterion has been upgraded by adding the possibility to rotate the quadrants. The offset angle selected, which is between 0 and 
+60 degrees, is the one that maximises the sum of the distances of the potential neighbours to their closest quadrant delimitation.
+
+In other words, it tends to select the angle with which the potential neighbors are as much in the middle of their respective quadrants
+as possible.
+
+The quadrant criterion is illustrated here Fig~\ref{fig:crit_qua}
 

### 2024-08-19 article.tex
adding content to the density part

@@
 \subsection{Measurement of \acrshort{bs} density}
-\noindent To make it easier to understand, and because it is related,
-we will assume that solving this problem is equivalent to finding the \acrshort{bs} situated in \og cities\fg{}.
+\noindent Places with a high population also have a high density of base stations. In fact, each base station can only support a certain
+load of users.
+
+Therefore, we can assume that finding zones with a high density of base station is equivalent to finding the \acrshort{bs} 
+situated in \og cities\fg{}.
 
@@
     \item \emph{extra-urban area};
-    \item \emph{courntryside}.
+    \item \emph{countryside}.
 \end{itemize}
@@
 \subsubsection{\acrshort{dbscan}}
-When thinking of density-based clustering, one of the first methods that comes in mind is probably \acrshort{dbscan}.
-It is really powerful because we only have two parameters to modify.
+The goal here is to separate points that seem to belong to a denser conglomerate of base station, from the others who are a bit more spaced
+to cover the countryside.
 
-Despite the efficiency of this method, it is not the best adapted to our problem because it's only giving us if a \acrshort{bs} is considered in a city or not.
-We wanted a more continuous method.
+That is called density based clustering. The main method to do that is \acrshort{dbscan}.
+
+It consists in detecting clusters based on the density, using two parameters :
+
+\begin{itemize}
+    \item \emph{$\epsilon$} : A distance threshold under which two points are considered close enough to be considered neighbours;   
+    \item \emph{$n_{\text{min}}$} : The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.
+
+\end{itemize}
+
+The clusters will then "grow" from the core points by attaching all points close from less than \emph{$epsilon$} than a point of the said 
+cluster.
+
+Despite the efficiency of this method, it is not the best adapted to our problem because it's only giving us if a \acrshort{bs} is considered 
+in a city or not, it doesn't split the points that are in a city into the four categories presented above.
 
 \subsubsection{\acrshort{hdbscan}}
+This method, introduced here \cite{10.1007/978-3-642-37456-2_14} is a variation of the \acrshort{dbscan} method. It consists
+in selecting the best clusters after testing their persistence by making the $\epsilon$ parameter vary. It's main particularity
+is that it allows to detect clusters of different densities.
+
+To each point who belong to a cluster is associated a probability that symbolises the degree of certainty for this point to belong
+to the said cluster.
+
+This probability can be used to separate the center of the city (where the probability is very high) from the rest of the city. However,
+it cannot be precise enough to separate the clusters into the four categories.
 
 \subsubsection{$3$-NN mean distance}
-To classify each base station we need a method.
+For our use case, we need a more specific method. Here is the explanation of how it works:
 
-For each base station the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in $\unit{km}$), thus making it possible to classify each base station into four different categories listed in Table~\ref{table:crit_summary}.
+For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in 
+$\unit{km}$). According to the value of $\gamma_i$, the base station can either be classified as part of one of the categroies of 
+Table~\ref{table:crit_summary} (very low value for city center, slighlty higher value for urban area,\dots).
 
-To make this method working properly, only \acrshort{bs} from one provider have to be kept into the calculation process.
-Moreover, this values are working well on France but it is not proven that it can work in another country. If someone uses this methods, values could be modified.
+To make this method work properly, only \acrshort{bs} from one provider have to be kept into the calculation process.
+
+Moreover, this values are working well on France but it is not proven that it can work in another country. If someone uses this methods, 
+values could be modified.
 
@@
         extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
-        courntryside & $\unit[15]{km}$ & $20^\circ$ \\
+        countryside & $\unit[15]{km}$ & $20^\circ$ \\
         \bottomrule

### 2024-08-19 article.tex
Ajout d'infos sur la database

--- 2024-08-16 article.tex
@@
     of the different approaches and conclude.
+
+    \textbf{WE WILL WORK WITH ONLY ONE PROVIDER [ptet le mettre ailleurs].}
 \section{Related works}
@@
 
-    \begin{table}[!t]
+    This database is updated every quarter. For instance, the own we used was published on 28th March 2024 \cite{main_database_hist}.
+
+    On the site there is a chat where we can ask questions about the databases \cite{main_database_chat}.
+
+    \begin{table}[!b]
         \centering
@@
 
+    \begin{figure}[!t]
+        \centering
+        \boxed{\includegraphics[width=2.5in]{images/data_analysis/with_techno.png}}
+        \caption{Breakdown, by operator, of the number of sites containing a given technology}
+        \label{fig:data_technos}
+    \end{figure}
+
 \begin{table}[!b]
@@
         \cmidrule(lr){1-2}
-        \textsl{BS\_anfr\_id} & \acrshort{anfr} \acrshort{bs} ID \\ 
+        \textsl{id\_station\_anfr} & \acrshort{anfr} \acrshort{bs} ID \\ 
+        \textsl{nom\_op} & Name of the provider \\
         \textsl{x, y, latitude, longitude} & Base station coordinates \\ 

### 2024-08-19 article.tex
Légère correction de mise en page

@@
 \begin{itemize}
-    \item \emph{$\epsilon$} : A distance threshold under which two points are considered close enough to be considered neighbours;   
+    \item \emph{$\varepsilon$} : A distance threshold under which two points are considered close enough to be considered neighbours;   
     \item \emph{$n_{\text{min}}$} : The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.
@@
 
-The clusters will then "grow" from the core points by attaching all points close from less than \emph{$epsilon$} than a point of the said 
+The clusters will then \og grow\fg{} from the core points by attaching all points close from less than \emph{$\varepsilon$} than a point of the said 
 cluster.
@@
 This method, introduced here \cite{10.1007/978-3-642-37456-2_14} is a variation of the \acrshort{dbscan} method. It consists
-in selecting the best clusters after testing their persistence by making the $\epsilon$ parameter vary. It's main particularity
+in selecting the best clusters after testing their persistence by making the $\varepsilon$ parameter vary. It's main particularity
 is that it allows to detect clusters of different densities.
@@
 $\unit{km}$). According to the value of $\gamma_i$, the base station can either be classified as part of one of the categroies of 
-Table~\ref{table:crit_summary} (very low value for city center, slighlty higher value for urban area,\dots).
+Table~\ref{table:crit_summary} (very low value for city center, slighlty higher value for urban area, \dots).
 

### 2024-08-19 article.tex
Correction formulation critère du quadratn

@@
 \subsubsection{Quadrant criterion}
-A version of this criterion was introduced here \cite{10201211} and used here \cite{art_del_paq}. Its goal is
-to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the 
+As introduced in a previous article \cite{10201211} its goal is to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the 
 $k$-NN potential neigbours method.
@@
 It consists in dividing the space around each base station into quadrants and keeping only a certain number of potential neighbours
-in each of the quadrants. The number of quadrants has been fixed to 6 (optimized here \cite{art_del_paq}).
+in each of the quadrants. The number of quadrants has been fixed to six \cite{art_del_paq}.
 
-The criterion has been upgraded by adding the possibility to rotate the quadrants. The offset angle selected, which is between 0 and 
-60 degrees, is the one that maximises the sum of the distances of the potential neighbours to their closest quadrant delimitation.
+The criterion has been upgraded by adding the possibility to rotate the quadrants. The offset angle selected, which is between $0$ and 
+$60$ degrees, is the one that maximises the sum of the distances of the potential neighbours to their closest quadrant delimitation.
 
@@
 
-The quadrant criterion is illustrated here Fig~\ref{fig:crit_qua}
+The quadrant criterion is illustrated in Fig~\ref{fig:crit_qua}.
 

### 2024-08-19 article.tex
Ajout de la filtration de la base

@@
     of the different approaches and conclude.
-
-    \textbf{WE WILL WORK WITH ONLY ONE PROVIDER [ptet le mettre ailleurs].}
 \section{Related works}
@@
             \cmidrule(lr){1-6}
-            \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
+            \textbf{2G} &You can 21710 & 0 & 18835 & 20093 & 60638 \\
             \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
@@
     \end{table}
+
+    \subsection{Filtering the database}
+    As seen before this database is really huge, as a matter of fact we will only work on a portion of it.
+
+    Firstly, only one provider will be kept because a \acrshort{bs} from provider $x$ can't be considered as a neighbour of \acrshort{bs} from provider $y$.
+    Consequently, we have chosen \emph{Orange} because it is the one that has the largest number of \acrshort{bs}.
+
+    Secondly, for the same reasons as before, only one technology is kept. Thus, we kept all \acrshort{bs} using, at least, $4G$.
 

### 2024-08-19 article.tex
Cahngement sur les auteurs (à finir)
Correction de fautes

@@
 \title{Adaptative neigbouring methods applied to telephonic base stations}
-\author{Paul MÉHAUD, Brendan SÉVELLEC}
+\author{\IEEEauthorblockN{Paul MÉHAUD}\\
+\IEEEauthorblockA{\textit{Intern at CTU in Prague} \\
+\textit{INSA Rouen Normandie}\\
+paul.mehaud@insa-rouen.fr}\\
+\and
+\IEEEauthorblockN{Brendan SÉVELLEC}\\
+\IEEEauthorblockA{\textit{Intern at CTU in Prague} \\
+\textit{INSA Rouen Normandie}\\
+brendan.sevellec@insa-rouen.fr}}
 
@@
 
-    This database is updated every quarter. For instance, the own we used was published on 28th March 2024 \cite{main_database_hist}.
+    This database is updated every quarter. For instance, the own we used was published on 28\textsuperscript{th} March 2024 \cite{main_database_hist}.
 
@@
             \cmidrule(lr){1-6}
-            \textbf{2G} &You can 21710 & 0 & 18835 & 20093 & 60638 \\
+            \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
             \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\

### 2024-08-20 article.tex
Changement d'indentation
Modification de partie 4

@@
     For that, it is necessary to describe and analyse the databases that have been used during the research, then to present 
-    the different approaches that always consist of these steps : establish a first neighbouring graph, compute the base station 
+    the different approaches that always consist of these steps: establish a first neighbouring graph, compute the base station 
     densities and filter this graph with different criteria using this information. The final step is to present the results
@@
 
-    The fields that are being used here are described in Table~\ref{table:data_columns}.
+The fields that are being used here are described in Table~\ref{table:data_columns}. [expliquer qu'il y x colonnes mais qu'on utilise que elles]
 
-    This database is updated every quarter. For instance, the own we used was published on 28\textsuperscript{th} March 2024 \cite{main_database_hist}.
+This database is updated every quarter. For instance, the own we used was published on 28\textsuperscript{th} March 2024 \cite{main_database_hist}. [dire depuis quand la base existe]
 
@@
 
+[parler des technologies, rajouter des graphes]
+
 \begin{table}[!b]
     \centering
-        \caption{Summary of technologies}
+    \caption{Number of \acrfull{bs} equipped, at least, with $x$G, by provider}
     \label{table:techno_numbers}
@@
     \centering
-        \caption{Description of the dataset}
+    \caption{Description of the main database columns used in the experiments}
     \label{table:data_columns}
@@
 
-    Secondly, for the same reasons as before, only one technology is kept. Thus, we kept all \acrshort{bs} using, at least, $4G$.
+Secondly, for the same reasons as before, only one technology is kept. Thus, we kept all \acrshort{bs} using, at least, 4G.
 
-\section{Finding potential neighbours}
-\noindent When we are looking for neighbours, we need, at first, a list of potential neighbours for each \acrfull{bs}.
-For that, we will construct a neigbouring graph $G = (P, U)$ (each base station that are considered neighbors are
-connected by an edge) where $P$ is the set of all base stations. 
-Here are the different methods we can build this graph with:
+Finally, in order to simplify viewing, we will apply our neighbouring only on the Normandie region just because this is where we live.
+\section{Reminder on existing methods}
+\subsection{Finding potential neighbours}
+\noindent When we are looking for neighbours, we need, at first, a list of potential neighbours for each point.
+For that, we will construct a neigbouring graph $G = (P, U)$ where $P$ is the set of all points and each edge in $U$ represents a neighbouring relation.
 
-\subsection{$k$-NN graph}
-\noindent The most intuitive method is to connect each \acrshort{bs} to its $k$ nearest neighbours, where $k \in \mathbb{N}^*$ 
-is a parameter to be fixed.
+\subsubsection{$k$-NN graph}
+The most intuitive method is to connect each point to its $k$ nearest neighbours, where $k \in \mathbb{N}^*$ is a parameter to be fixed.
 
-However, this method can be criticized, because it always finds $k$ neighbor to each base stations, no matter the reality of the 
+However, this method can be criticised, because it always finds $k$ neighbours for each point, no matter the reality of the 
 data.
 
-\subsection{Delaunay triangulation}
-\noindent The Delaunay triangulation is named after Boris DELAUNAY for his work on it from 1934 \cite{art_delaunay}.
-
-A Delaunay triangulation of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles 
-do not contain any of the points. You can find an illustration of this method in Figure~\ref{fig:del_tri}.
+\subsubsection{Delaunay triangulation}
+A Delaunay triangulation \cite{art_delaunay} of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles 
+do not contain any of the points.
 
@@
 
-The Delaunay triangulation is the pendant of the Voronoi diagram in the sense that two points are connected in the
-Delaunay triangulation if their associated cells share an edge in the Voronoi diagram.
-
-Therefore, another approach, consists in computing a Delaunay triangulation and build a neighouring graph $G = (P, U)$ where $U$ 
-is composed of every edge of $D(P)$. Which is equivalent to consider two base station as potential neighbors if their associated
-cells are touching each other in the Voronoi diagram.
-
-This method has already been used in articles in the past \cite{delaunay_neighbor}.
+It is a well-known method when trying to find neighbours \cite{delaunay_neighbor}
+since a Delaunay triangulation is the pendant of a Voronoi diagram, cf. Figure~\ref{fig:del_tri}, i.e. two points are connected in the
+Delaunay triangulation if their associated cells are touching each other in the Voronoi diagram.
 
@@
     \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_Voronoi.png}}
-    \caption{Example of a Delaunay triangulation (in black) and Voronoi tessellation (in red)}
+    \caption{Example of a Delaunay triangulation (in black) and Voronoi diagram (in red)}
     \label{fig:del_tri}
@@
 
-\subsection{Gabriel graph}
-\noindent The Gabriel graph is a subgraph of a Delaunay triangulation. Thus, if the Delaunay triangulation is given, it can be found in a linear time.
+\subsubsection{Gabriel graph}
+A Gabriel graph \cite{10.2307/2412323} is a subgraph of a Delaunay triangulation. Thus, if the Delaunay triangulation is given, it can be found in a linear time.
 
-Gabriel graphs are named after K. Ruben Gabriel, who introduced them in a paper with Robert R. Sokal in 1969 \cite{10.2307/2412323}.
-
-Formally, it is the graph $G = (P, U)$ in which any two distinct points $p, q \in P$ are adjacent precisely when the closed disc having $pq$ as a diameter contains no other points.
+Formally, it is the graph in which any two distinct points $p, q \in P$ are adjacent precisely when the closed disc having $pq$ as a diameter contains no other points.
 
 Basically, the interset of this method, compared to the Delaunay triangulation, is that it is adding a first level of filtration to suppress some neighbouring connexions.
+
+\subsection{Finding real neighbours}
+\noindent For the purpose of our experiments, i.e. finding \acrshort{bs} neighbours, the previously presented methods are not sufficient to find real neighbours.
+As a consequence, some neighbouring connexions needs to be suppressed \cite{patent_neighs}.
+\subsubsection{Distance criterion\cite{patent_neighs}}
+A \acrshort{bs} does not have an infinite coverage area.
+As a consequence, each edge in $U$ that is longer than a certain value, called \emph{max\_distance}, is suppressed.
+
+\subsubsection{Angle criterion}
+Let $p$, $q$, $r$ be three \acrshort{bs} of $P$, where $q$ and $r$ are $p$'s potential neighbours.
+As said before, coverage areas of \acrshort{bs} are limited by physics, this also implies that $r$ can be \og hidden\fg{} from $p$ by $q$ because $q$ is between $p$ and $r$ [trouver qqch pour prouver ce que je dis].
+
+Therefore, the connexion between $p$ and $r$ needs to be suppressed.
+How?
+The angle $\widehat{qrp}$ is calculated and if it is narrower than a certain value, called \emph{min\_angle}, the longest edge is suppressed.
+
+\subsubsection{Quadrant criterion}
+\begin{figure}[!b]
+    \centering
+    \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
+    \caption{Example of a Delaunay triangulation}
+    \label{fig:crit_qua}
+\end{figure}
+
+As introduced in a previous article \cite{10201211} its goal is to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the 
+$k$-NN potential neigbours method.
+
+It consists in dividing the space around each base station into quadrants and keeping only a certain number of potential neighbours
+in each of the quadrants, cf. Figure~\ref{fig:crit_qua}.
+The number of quadrants has been fixed to six \cite{art_del_paq}.
+
+\subsection{Density-based clustering methods}
+\noindent Although the filtering methods are providing good results, it is still not enough.
+Therefore, we will modify those criteria to take in account the variations of \acrshort{bs} density. Thus, we need some measurement of this density.
+
+As those problems are equivalent and because this is simpler to visualise, we will say that we are looking for detecting the cities.
+\subsubsection{\acrshort{dbscan}}
+\acrshort{dbscan} consists in detecting clusters based on the density of points, using two parameters:
+\begin{itemize}
+    \item \emph{$\varepsilon$}: A distance threshold under which two points are considered close enough to be considered neighbours;   
+    \item \emph{$n_{\text{min}}$}: The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.
+\end{itemize}
+
+The clusters will then \og grow\fg{} from the core points by attaching all points close from less than \emph{$\varepsilon$} than a point of the said 
+cluster.
+
+\subsubsection{\acrshort{hdbscan}}
+\acrshort{hdbscan} \cite{10.1007/978-3-642-37456-2_14} is a variation of the \acrshort{dbscan} method. It consists
+in selecting the best clusters after testing their persistence by making the $\varepsilon$ parameter vary. It's main particularity
+is that it allows to detect clusters of different densities.
+
+To each point who belongs to a cluster is associated a probability that symbolises the degree of certainty for this point to belong
+to the said cluster.
 
@@
 
-Moreover, to simplify the problem, each \acrshort{bs} will be classified in one of this four categories :
+Moreover, to simplify the problem, each \acrshort{bs} will be classified in one of this four categories:
 \begin{itemize}
@@
 
-It consists in detecting clusters based on the density, using two parameters :
+It consists in detecting clusters based on the density, using two parameters:
 
 \begin{itemize}
-    \item \emph{$\varepsilon$} : A distance threshold under which two points are considered close enough to be considered neighbours;   
-    \item \emph{$n_{\text{min}}$} : The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.
-
+    \item \emph{$\varepsilon$}: A distance threshold under which two points are considered close enough to be considered neighbours;   
+    \item \emph{$n_{\text{min}}$}: The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.
 \end{itemize}
@@
 Moreover, this values are working well on France but it is not proven that it can work in another country. If someone uses this methods, 
-values could be modified.
+values could be modified [dire que c'est plutot qqch à faire dans le futur et pas que c'est pas vérifié].
+
+[Rajouter les catégories]
 
@@
 
-\begin{figure}[!b]
-    \centering
-    \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
-    \caption{Example of a Delaunay triangulation}
-    \label{fig:crit_qua}
-\end{figure}
-
 \begin{figure}[!t]
@@
 Table~\ref{table:crit_summary}), the longest edge is suppressed.
+
+[Dire que c'est des angles adjacents]
 
@@
 
-[Ouverture : prendre en compte les zazimuths]
+[Ouverture: prendre en compte les zazimuths]
 

### 2024-08-20 article.tex
Modification emplacement images et indentations

@@
 \section{Databases}
-Several databases have been used in order to test the different aspects of the methods. However, one of
+\noindent Several databases have been used in order to test the different aspects of the methods. However, one of
 them is directly necessary to the method itself.
@@
 The fields that are being used here are described in Table~\ref{table:data_columns}. [expliquer qu'il y x colonnes mais qu'on utilise que elles]
-
-This database is updated every quarter. For instance, the own we used was published on 28\textsuperscript{th} March 2024 \cite{main_database_hist}. [dire depuis quand la base existe]
-
-On the site there is a chat where we can ask questions about the databases \cite{main_database_chat}.
-
-[parler des technologies, rajouter des graphes]
-
-\begin{table}[!b]
-    \centering
-    \caption{Number of \acrfull{bs} equipped, at least, with $x$G, by provider}
-    \label{table:techno_numbers}
-    \begin{tabular}{cccccc}
-        \toprule
-        \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
-        \cmidrule(lr){1-6}
-        \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
-        \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
-        \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
-        \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
-        \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
-        \bottomrule
-    \end{tabular}
-\end{table}
-
-\begin{figure}[!t]
-    \centering
-    \boxed{\includegraphics[width=2.5in]{images/data_analysis/with_techno.png}}
-    \caption{Breakdown, by operator, of the number of sites containing a given technology}
-    \label{fig:data_technos}
-\end{figure}
-
 \begin{table}[!b]
@@
 
+This database is updated every quarter. For instance, the own we used was published on 28\textsuperscript{th} March 2024 \cite{main_database_hist}. [dire depuis quand la base existe]
+
+On the site there is a chat where we can ask questions about the databases \cite{main_database_chat}.
+
+[parler des technologies, rajouter des graphes]
+
+\begin{table}[!t]
+    \centering
+    \caption{Number of \acrfull{bs} equipped, at least, with $x$G, by provider}
+    \label{table:techno_numbers}
+    \begin{tabular}{cccccc}
+        \toprule
+        \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
+        \cmidrule(lr){1-6}
+        \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
+        \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
+        \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
+        \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
+        \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+\begin{figure}[!b]
+    \centering
+    \boxed{\includegraphics[width=2.5in]{images/data_analysis/with_techno.png}}
+    \caption{Breakdown, by operator, of the number of sites containing a given technology}
+    \label{fig:data_technos}
+\end{figure}
+
 \subsection{Filtering the database}
@@
 \subsection{Finding potential neighbours}
-\noindent When we are looking for neighbours, we need, at first, a list of potential neighbours for each point.
+When we are looking for neighbours, we need, at first, a list of potential neighbours for each point.
 For that, we will construct a neigbouring graph $G = (P, U)$ where $P$ is the set of all points and each edge in $U$ represents a neighbouring relation.
@@
 
-\begin{figure}[!t]
+\begin{figure}[!b]
     \centering
@@
 \subsection{Finding real neighbours}
-\noindent For the purpose of our experiments, i.e. finding \acrshort{bs} neighbours, the previously presented methods are not sufficient to find real neighbours.
+For the purpose of our experiments, i.e. finding \acrshort{bs} neighbours, the previously presented methods are not sufficient to find real neighbours.
 As a consequence, some neighbouring connexions needs to be suppressed \cite{patent_neighs}.
@@
 \subsection{Density-based clustering methods}
-\noindent Although the filtering methods are providing good results, it is still not enough.
+Although the filtering methods are providing good results, it is still not enough.
 Therefore, we will modify those criteria to take in account the variations of \acrshort{bs} density. Thus, we need some measurement of this density.
@@
 \subsection{Measurement of \acrshort{bs} density}
-\noindent Places with a high population also have a high density of base stations. In fact, each base station can only support a certain
+Places with a high population also have a high density of base stations. In fact, each base station can only support a certain
 load of users.

### 2024-08-20 article.tex
Suppression d'une phrase de liaison inutile

@@
 \subsection{Density-based clustering methods}
-Although the filtering methods are providing good results, it is still not enough.
-Therefore, we will modify those criteria to take in account the variations of \acrshort{bs} density. Thus, we need some measurement of this density.
-
-As those problems are equivalent and because this is simpler to visualise, we will say that we are looking for detecting the cities.
 \subsubsection{\acrshort{dbscan}}
@@
 
-\section{Finding the real neighbours}
-\noindent Each of the precedent methods gives us a list of potential neighbours for each \acrshort{bs}. However, we know that some of this neighbouring connexions are wrong,
+\section{Contributions}
+\noindent Each of the precedent methods gives us a list of potential neighbours for each \acrshort{bs}.
+However, we know that some of this neighbouring connexions are wrong,
 either because of the neighboring graph construction method or physical specificities linked to the base stations themselves.

### 2024-08-20 article.tex
Modification partie 5 (en cours)

@@
 Finally, in order to simplify viewing, we will apply our neighbouring only on the Normandie region just because this is where we live.
-\section{Reminder on existing methods}
+\section{Reminder on existing methods\label{sec:reminder}}
 \subsection{Finding potential neighbours}
@@
 \section{Contributions}
-\noindent Each of the precedent methods gives us a list of potential neighbours for each \acrshort{bs}.
-However, we know that some of this neighbouring connexions are wrong,
-either because of the neighboring graph construction method or physical specificities linked to the base stations themselves.
+\noindent In section~\ref{sec:reminder}, we have seen that we can find the neighbours of base stations
+by combining a potential neighbouring graph and filtration criteria. This methodology gives pretty good results \cite{art_del_paq}.
 
-Thus, we need to find methods to detetect and erase these bad connexions.
-
-The main innovation of our work compared to this one \cite{art_del_paq} is to take in account the difference of \acrshort{bs}'s density.
+However, in certain cases like in a city, the filtration criteria aren't precise enough. We, therefore, need to find some ways to measure base stations' density.
 
@@
 \subsubsection{\acrshort{dbscan}}
-The goal here is to separate points that seem to belong to a denser conglomerate of base station, from the others who are a bit more spaced
-to cover the countryside.
-
-That is called density based clustering. The main method to do that is \acrshort{dbscan}.
-
-It consists in detecting clusters based on the density, using two parameters:
-
-\begin{itemize}
-    \item \emph{$\varepsilon$}: A distance threshold under which two points are considered close enough to be considered neighbours;   
-    \item \emph{$n_{\text{min}}$}: The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.
-\end{itemize}
-
-The clusters will then \og grow\fg{} from the core points by attaching all points close from less than \emph{$\varepsilon$} than a point of the said 
-cluster.
-
-Despite the efficiency of this method, it is not the best adapted to our problem because it's only giving us if a \acrshort{bs} is considered 
-in a city or not, it doesn't split the points that are in a city into the four categories presented above.
+DBScan gives only two categories : city - countryside
+[permet de faire que 2 categories : pas assez précis (mais ptet à mettre dans résultats)]
 
 \subsubsection{\acrshort{hdbscan}}
-This method, introduced here \cite{10.1007/978-3-642-37456-2_14} is a variation of the \acrshort{dbscan} method. It consists
-in selecting the best clusters after testing their persistence by making the $\varepsilon$ parameter vary. It's main particularity
-is that it allows to detect clusters of different densities.
-
-To each point who belong to a cluster is associated a probability that symbolises the degree of certainty for this point to belong
-to the said cluster.
-
-This probability can be used to separate the center of the city (where the probability is very high) from the rest of the city. However,
-it cannot be precise enough to separate the clusters into the four categories.
+...
 
@@
 
-\subsection{Filtering criteria}
+\subsection{Improvement of filtering criteria}
 

### 2024-08-20 article.tex
Modification 3-NN

@@
 
-Moreover, to simplify the problem, each \acrshort{bs} will be classified in one of this four categories:
-\begin{itemize}
-    \item \emph{city center};
-    \item \emph{urban area};
-    \item \emph{extra-urban area};
-    \item \emph{countryside}.
-\end{itemize}
-
 \subsubsection{\acrshort{dbscan}}
@@
 \subsubsection{$3$-NN mean distance}
-For our use case, we need a more specific method. Here is the explanation of how it works:
-
 For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in 
 $\unit{km}$). According to the value of $\gamma_i$, the base station can either be classified as part of one of the categroies of 
-Table~\ref{table:crit_summary} (very low value for city center, slighlty higher value for urban area, \dots).
+Table~\ref{table:crit_summary}:
+\begin{itemize}
+    \item city center: $\gamma_i\in [0,1]$;
+    \item urban area: $\gamma_i\in ]1,2]$;
+    \item extra-urban: $\gamma_i\in ]2,4]$;
+    \item countryside: $\gamma_i\in ]4,\infty[$.
+\end{itemize}
 
-To make this method work properly, only \acrshort{bs} from one provider have to be kept into the calculation process.
+To make this method work properly, only \acrshort{bs} from the same provider have to be kept into the calculation process.
 
-Moreover, this values are working well on France but it is not proven that it can work in another country. If someone uses this methods, 
-values could be modified [dire que c'est plutot qqch à faire dans le futur et pas que c'est pas vérifié].
-
-[Rajouter les catégories]
+Althought, this values are working well on France, we haven't tried yet on another country.
 
@@
 
+\subsection{Measurement of \acrshort{bs} density}
+
 \subsection{Combining criteria}

### 2024-08-20 article.tex
Ajout critères améliorés

@@
 \subsubsection{Quadrant criterion}
-\begin{figure}[!b]
-    \centering
-    \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
-    \caption{Example of a Delaunay triangulation}
-    \label{fig:crit_qua}
-\end{figure}
-
 As introduced in a previous article \cite{10201211} its goal is to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the 
@@
 For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in 
-$\unit{km}$). According to the value of $\gamma_i$, the base station can either be classified as part of one of the categroies of 
-Table~\ref{table:crit_summary}:
+$\unit{km}$). According to the value of $\gamma_i$, the base station can either be classified into one of these categories:
 \begin{itemize}
@@
 \end{itemize}
-
-To make this method work properly, only \acrshort{bs} from the same provider have to be kept into the calculation process.
-
-Althought, this values are working well on France, we haven't tried yet on another country.
+If you want this method to work properly, only \acrshort{bs} from the same provider have to be kept into the calculation process.
+Althought this values are working well on France, we haven't tried yet on another country.
 
 \subsection{Improvement of filtering criteria}
-
-\begin{table}[!b]
+\begin{table}[!t]
     \centering
@@
 
-\begin{figure}[!t]
-    \centering
-    \boxed{\includegraphics[width=2.5in]{images/illus_crit/points.png}}
-    \caption{Example of a Delaunay triangulation}
-    \label{fig:crit_pts}
-\end{figure}
+\subsubsection{Distance and angle criterion}
+As seen in section~\ref{sec:reminder}, after having found potential neighbours for each base station,
+we need to filtrate this connexions. However, this applies the same distance and angle threshold for all base stations, without taking in account the difference of density.
 
-\begin{figure}[!b]
-    \centering
-    \boxed{\includegraphics[width=2.5in]{images/illus_crit/distance_elim.png}}
-    \caption{Example of a Delaunay triangulation}
-    \label{fig:crit_dis}
-\end{figure}
+The method we propose now is to take in account those differences of density for each site to apply a different thresholdn according to the category the site in classified in.
 
-\begin{figure}[!t]
-    \centering
-    \boxed{\includegraphics[width=2.5in]{images/illus_crit/angle_elim.png}}
-    \caption{Example of a Delaunay triangulation}
-    \label{fig:crit_ang}
-\end{figure}
-
-\begin{figure}[!t]
-    \centering
-    \boxed{\includegraphics[width=2.5in]{images/illus_crit/neighs.png}}
-    \caption{Example of a Delaunay triangulation}
-    \label{fig:crit_nei}
-\end{figure}
-
-\subsubsection{Distance criterion}
-When looking at the results of Delaunay triangulation, we realise that some edges, mostly on the border of $P$ are too long.
-
-Indeed, a \acrshort{bs} does not have an infinite coverage area.
-As a consequence, for each \acrshort{bs} the neighbouring connexions that are longer than a certain value, called \emph{max\_distance} (cf.
-Table~\ref{table:crit_summary}), are suppressed.
-
-\subsubsection{Angle criterion}
-Let $p$, $q$, $r$ be three \acrshort{bs} of $P$, where $q$ and $r$ are $p$'s potential neighbours.
-As said before, coverage areas of \acrshort{bs} are limited by physics, this also implies that $r$ can be \og hidden\fg{} from $p$ by $q$ because $q$ is between $p$ and $r$ [trouver qqch pour prouver ce que je dis].
-
-Therefore, the connexion between $p$ and $r$ needs to be suppressed.
-How?
-The angle $\widehat{qrp}$ is calculated and if it is narrower than a certain value, called \emph{min\_angle} (cf.
-Table~\ref{table:crit_summary}), the longest edge is suppressed.
-
-[Dire que c'est des angles adjacents]
+You can find those values listed in Table~\ref{table:crit_summary}.
 
 \subsubsection{Quadrant criterion}
-As introduced in a previous article \cite{10201211} its goal is to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the 
-$k$-NN potential neigbours method.
-
-It consists in dividing the space around each base station into quadrants and keeping only a certain number of potential neighbours
-in each of the quadrants. The number of quadrants has been fixed to six \cite{art_del_paq}.
-
-The criterion has been upgraded by adding the possibility to rotate the quadrants. The offset angle selected, which is between $0$ and 
+This criterion has been upgraded by adding the possibility to rotate the quadrants. The offset angle selected, which is between $0$ and 
 $60$ degrees, is the one that maximises the sum of the distances of the potential neighbours to their closest quadrant delimitation.
@@
 The quadrant criterion is illustrated in Fig~\ref{fig:crit_qua}.
+\begin{figure}[!t]
+    \centering
+    \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
+    \caption{Illustation of the rotated quadrant criterion}
+    \label{fig:crit_qua}
+\end{figure}
 

### 2024-08-20 article.tex
beginning to remake the introduction

--- 2024-08-20 article.tex
@@
     companies to predict their customers behaviour for internal or marketing purposes. Thus, it is primordial for these companies
-  to be able to determinate if a user is moving. For that, it is necessary to understand the neighbouring relationships between the 
-  telephonic base stations. This article aims at comparing different method, ellaborated in order to adaptively detect these
-  relationship between telephonic base stations given their geographical positions.
+    to be able to determine if a user is moving. For that, it is necessary to understand the neighbouring relationships between the 
+    telephonic base stations. This article aims at proposing and comparing different method, that aim at adaptively detect these
+    relationship between telephonic base stations. Therefore, it proposes a new method to create a neighbouring graph of base
+    stations via their geographical positions.
 \end{abstract}
@@
 \section{Introduction}
-    \IEEEPARstart{T}{his} article is the continuation of the work done by Delphine Paquiry in this paper \cite{art_del_paq}.
-    It aims at discovering the neighbouring relationships between base stations from their geographical positions, using a 
-    measure of the density of base station.
+    \IEEEPARstart{T}{his} article articulates around the themes of mobile networks and neighbouring problems.
 
-    For that, it is necessary to describe and analyse the databases that have been used during the research, then to present 
-    the different approaches that always consist of these steps: establish a first neighbouring graph, compute the base station 
-    densities and filter this graph with different criteria using this information. The final step is to present the results
-    of the different approaches and conclude.
+    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known 
+    as cells, each of which is supplied by at least one fixed-location transceiver called base station. These base stations give the cell network
+    coverage so that voice, data, and other kinds of content may be transmitted.
+
+    Given a list of points and their coordinates, a neighbouring problem consists in finding, for each point, a list of other points that are 
+    considered as its neighbours.
+
 \section{Related works}
@@
 This database \cite{main_database} contains all the information needed to the application of the method. It is from
-\acrfull{arcep}, which is an independent French administrative authority responsible for regulating electronic and postal communications and press distribution.
+\acrfull{arcep}, which is an independent French administrative authority responsible for regulating electronic and postal 
+communications and press distribution.
 

### 2024-08-20 article.tex
Ajouts sur la data, suppression des emplacements figures et tab, modif sur 3-NN et ses amis

--- 2024-08-20 article.tex
@@
 \subsection{Main database}
-This database \cite{main_database} contains all the information needed to the application of the method. It is from
+This database \cite{main_database} contains all the information needed for the application of the method. It is from
 \acrfull{arcep}, which is an independent French administrative authority responsible for regulating electronic and postal communications and press distribution.
 
-The fields that are being used here are described in Table~\ref{table:data_columns}. [expliquer qu'il y x colonnes mais qu'on utilise que elles]
-\begin{table}[!b]
+This database was first published for the third quarter of 2017 and the version we are using was published on 28\textsuperscript{th} March 2024 \cite{main_database_hist}.
+It's updated for every quarter. For instance, the data we used refers to the fourth quarter of 2023.
+
+It consists of a substantial collection of $108\,838$ entries, encompassing 29 distinct features of a size of $\unit[16.7]{Mo}$.
+Each row of the database corresponds to detailed information regarding a specific BS. For the scope of this study,
+our analysis will focus on the fields outlined in Table~\ref{table:data_columns}.
+\begin{table}
     \centering
@@
         \textsl{nom\_op} & Name of the provider \\
-        \textsl{x, y, latitude, longitude} & Base station coordinates \\ 
+        \textsl{$x$, $y$, latitude, longitude} & Base station coordinates \\ 
         \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
@@
 
-This database is updated every quarter. For instance, the own we used was published on 28\textsuperscript{th} March 2024 \cite{main_database_hist}. [dire depuis quand la base existe]
+For station coordinates, we will use two different reference points: $x$ and $y$ coordinates, which are Lambert-93 projections of latitude and longitude.
+This dual system has two advantages: the $x$, $y$ coordinates allow us to calculate distances in meters using the Euclidean norm,
+which is more efficient in terms of calculation, and the GPS coordinates make it easier to display the points on a map.
 
-On the site there is a chat where we can ask questions about the databases \cite{main_database_chat}.
+In addition, we can find in the columns the name of the provider (\textsl{nom\_op}). In this database, only the four main french providers are represented:
+\emph{Bouygues Telecom}, \emph{Free Mobile}, \emph{Orange} and \emph{SFR}.
 
-[parler des technologies, rajouter des graphes]
-
-\begin{table}[!t]
+Finally, we have informations about the technologies used in every site. Indeed, a site can use multiple technologies.
+In Figure~\ref{fig:data_evolution} you will find the evolution of each technology from the first updates of the data.
+\begin{figure}
+    \centering
+    \boxed{\includegraphics[width=2.5in]{images/data_analysis/technos-evolution.png}}
+    \caption{Evolution by quarter year and by technology of the number of \acrshort{bs}}
+    \label{fig:data_evolution}
+\end{figure}
+Then, in Figure~\ref{fig:data_technos} you will find a chart showing the number of times each technology is present for each provider.
+\begin{figure}
+    \centering
+    \boxed{\includegraphics[width=2.5in]{images/data_analysis/with_techno.png}}
+    \caption{Breakdown, by operator, of the number of sites containing a given technology}
+    \label{fig:data_technos}
+\end{figure}
+We can see, for example, that \emph{Free Mobile} doesn't have any base station with $2$G technology. Additionally, you can als find these values in Table~\ref{table:techno_numbers}.
+\begin{table}
     \centering
@@
 
-\begin{figure}[!b]
-    \centering
-    \boxed{\includegraphics[width=2.5in]{images/data_analysis/with_techno.png}}
-    \caption{Breakdown, by operator, of the number of sites containing a given technology}
-    \label{fig:data_technos}
-\end{figure}
-
 \subsection{Filtering the database}
@@
 
-Finally, in order to simplify viewing, we will apply our neighbouring only on the Normandie region just because this is where we live.
+In order to simplify the calculation times, the vision and the assessment of the quality of the results, we will only work on sites located in the Normandy region.
+This is because Normandy is where our school is based, giving us a better view of its geography.
+
 \section{Reminder on existing methods\label{sec:reminder}}
@@
 
-\begin{figure}[!b]
+\begin{figure}
     \centering
@@
 For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in 
-$\unit{km}$). According to the value of $\gamma_i$, the base station can either be classified into one of these categories:
-\begin{itemize}
-    \item city center: $\gamma_i\in [0,1]$;
-    \item urban area: $\gamma_i\in ]1,2]$;
-    \item extra-urban: $\gamma_i\in ]2,4]$;
-    \item countryside: $\gamma_i\in ]4,\infty[$.
-\end{itemize}
+$\unit{km}$). According to the value of $\gamma_i$, the base station will be classified into a different category.
+
 If you want this method to work properly, only \acrshort{bs} from the same provider have to be kept into the calculation process.
@@
 
+% \begin{itemize}
+%     \item city center: $\gamma_i\in [0,1]$;
+%     \item urban area: $\gamma_i\in ]1,2]$;
+%     \item extra-urban: $\gamma_i\in ]2,4]$;
+%     \item countryside: $\gamma_i\in ]4,\infty[$.
+% \end{itemize}
+
 \subsection{Improvement of filtering criteria}
-\begin{table}[!t]
+\begin{table}
     \centering
@@
 
-The method we propose now is to take in account those differences of density for each site to apply a different thresholdn according to the category the site in classified in.
+The method we propose now is to take in account those differences of density for each site to apply a different threshold according to the category the site in classified in.
 
-You can find those values listed in Table~\ref{table:crit_summary}.
+For both distance and angle, the more the base station is in a dense category, the lower this threshold will be.
 
@@
 The quadrant criterion is illustrated in Fig~\ref{fig:crit_qua}.
-\begin{figure}[!t]
+\begin{figure}
     \centering

### 2024-08-20 article.tex

@@
 This database \cite{main_database} contains all the information needed for the application of the method. It is from
-\acrfull{arcep}, which is an independent French administrative authority responsible for regulating electronic and postal communications and press distribution.
+\acrfull{arcep}, which is an independent French administrative authority responsible for regulating electronic and postal 
+communications and press distribution.
 

### 2024-08-21 article.tex
Correction d'un bout de mise en page

@@
 
-It consists of a substantial collection of $108\,838$ entries, encompassing 29 distinct features of a size of $\unit[16.7]{Mo}$.
+It consists of a substantial collection of $108\,838$ entries, encompassing $29$ distinct features of a size of $\unit[16.7]{Mo}$.
 Each row of the database corresponds to detailed information regarding a specific BS. For the scope of this study,
@@
 
-\subsection{Filtering the database}
+\subsection{Filtering the main database}
 As seen before this database is really huge, as a matter of fact we will only work on a portion of it.
@@
 This is because Normandy is where our school is based, giving us a better view of its geography.
+
+\subsection{Additional database}
+In order to compare the results of city detection, we needed a reference database. We therefore used the population data provided by INSEE.
+[Pas sur de l'utilité de présenter cette base en fait, ptet juste la principale suffit]
 

### 2024-08-21 article.tex
Revert "Correction d'un bout de mise en page"
This reverts commit 6110e6c9fbb40ba0c6afd953317f3e0f3cc515c8.
Correction d'un bout de mise en page
Reprise mise en page du code

@@
 \begin{abstract}
-    The field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\%
-    in 2023 in the world, and 97\% in France. Therefore, the collected datas represent a big opportunity for telecommunication
-    companies to predict their customers behaviour for internal or marketing purposes. Thus, it is primordial for these companies
-    to be able to determine if a user is moving. For that, it is necessary to understand the neighbouring relationships between the 
-    telephonic base stations. This article aims at proposing and comparing different method, that aim at adaptively detect these
-    relationship between telephonic base stations. Therefore, it proposes a new method to create a neighbouring graph of base
-    stations via their geographical positions.
+    The field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\% in 2023 in the world, and 97\% in France.
+Therefore, the collected datas represent a big opportunity for telecommunication companies to predict their customers behaviour for internal or marketing purposes.
+Thus, it is primordial for these companies to be able to determine if a user is moving.
+For that, it is necessary to understand the neighbouring relationships between the telephonic base stations.
+This article aims at proposing and comparing different method, that aim at adaptively detect these relationship between telephonic base stations.
+Therefore, it proposes a new method to create a neighbouring graph of base stations via their geographical positions.
 \end{abstract}
@@
 
-    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known 
-    as cells, each of which is supplied by at least one fixed-location transceiver called base station. These base stations give the cell network
-    coverage so that voice, data, and other kinds of content may be transmitted.
+    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known as cells, each of which is supplied by at least one fixed-location transceiver called base station.
+These base stations give the cell network coverage so that voice, data, and other kinds of content may be transmitted.
 
-    Given a list of points and their coordinates, a neighbouring problem consists in finding, for each point, a list of other points that are 
-    considered as its neighbours.
+    Given a list of points and their coordinates, a neighbouring problem consists in finding, for each point, a list of other points that are considered as its neighbours.
 
 \section{Related works}
+    \noindent
 
 \section{Databases}
-\noindent Several databases have been used in order to test the different aspects of the methods. However, one of
-them is directly necessary to the method itself.
+    \noindent Several databases have been used in order to test the different aspects of the methods. However, one of them is directly necessary to the method itself.
 
     \subsection{Main database}
-This database \cite{main_database} contains all the information needed for the application of the method. It is from
-\acrfull{arcep}, which is an independent French administrative authority responsible for regulating electronic and postal 
-communications and press distribution.
+        This database \cite{main_database} contains all the information needed for the application of the method.
+It is from \acrfull{arcep}, which is an independent French administrative authority responsible for regulating electronic and postal communications and press distribution.
 
@@
         It consists of a substantial collection of $108\,838$ entries, encompassing $29$ distinct features of a size of $\unit[16.7]{Mo}$.
-Each row of the database corresponds to detailed information regarding a specific BS. For the scope of this study,
-our analysis will focus on the fields outlined in Table~\ref{table:data_columns}.
+        Each row of the database corresponds to detailed information regarding a specific BS.
+For the scope of this study, our analysis will focus on the fields outlined in Table~\ref{table:data_columns}.
         \begin{table}
@@
         For station coordinates, we will use two different reference points: $x$ and $y$ coordinates, which are Lambert-93 projections of latitude and longitude.
-This dual system has two advantages: the $x$, $y$ coordinates allow us to calculate distances in meters using the Euclidean norm,
-which is more efficient in terms of calculation, and the GPS coordinates make it easier to display the points on a map.
+        This dual system has two advantages: the $x$, $y$ coordinates allow us to calculate distances in meters using the Euclidean norm, which is more efficient in terms of calculation, and the GPS coordinates make it easier to display the points on a map.
 
@@
         In order to compare the results of city detection, we needed a reference database. We therefore used the population data provided by INSEE.
-[Pas sur de l'utilité de présenter cette base en fait, ptet juste la principale suffit]
+        [Pas sûr de l'utilité de présenter cette base en fait, ptet juste la principale suffit]
 
@@
 
-However, this method can be criticised, because it always finds $k$ neighbours for each point, no matter the reality of the 
-data.
+            However, this method can be criticised, because it always finds $k$ neighbours for each point, no matter the reality of the data.
 
         \subsubsection{Delaunay triangulation}
-A Delaunay triangulation \cite{art_delaunay} of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles 
-do not contain any of the points.
+            A Delaunay triangulation \cite{art_delaunay} of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles do not contain any of the points.
 
-A Voronoi diagram is a tessellation pattern in which $n$ points scattered on a plane subdivides in 
-exactly $n$ cells enclosing a portion of the plane that is closest to each point.
+            A Voronoi diagram is a tessellation pattern in which $n$ points scattered on a plane subdivides in exactly $n$ cells enclosing a portion of the plane that is closest to each point.
 
-It is a well-known method when trying to find neighbours \cite{delaunay_neighbor}
-since a Delaunay triangulation is the pendant of a Voronoi diagram, cf. Figure~\ref{fig:del_tri}, i.e. two points are connected in the
+            It is a well-known method when trying to find neighbours \cite{delaunay_neighbor} since a Delaunay triangulation is the pendant of a Voronoi diagram, cf.
+Figure~\ref{fig:del_tri}, i.e.
+two points are connected in the
             Delaunay triangulation if their associated cells are touching each other in the Voronoi diagram.
@@
         As a consequence, some neighbouring connexions needs to be suppressed \cite{patent_neighs}.
-\subsubsection{Distance criterion\cite{patent_neighs}}
+        \subsubsection{Distance criterion}
             A \acrshort{bs} does not have an infinite coverage area.
@@
         \subsubsection{Quadrant criterion}
-As introduced in a previous article \cite{10201211} its goal is to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the 
-$k$-NN potential neigbours method.
+            As introduced in a previous article \cite{10201211} its goal is to prevent all potential neighbours to be in the same angle range.
+Therefore, it was mainly thought to be used with the $k$-NN potential neigbours method.
 
-It consists in dividing the space around each base station into quadrants and keeping only a certain number of potential neighbours
-in each of the quadrants, cf. Figure~\ref{fig:crit_qua}.
+            It consists in dividing the space around each base station into quadrants and keeping only a certain number of potential neighbours in each of the quadrants, cf. Figure~\ref{fig:crit_qua}.
             The number of quadrants has been fixed to six \cite{art_del_paq}.
@@
 
-The clusters will then \og grow\fg{} from the core points by attaching all points close from less than \emph{$\varepsilon$} than a point of the said 
-cluster.
+            The clusters will then \og grow\fg{} from the core points by attaching all points close from less than \emph{$\varepsilon$} than a point of the said cluster.
 
         \subsubsection{\acrshort{hdbscan}}
-\acrshort{hdbscan} \cite{10.1007/978-3-642-37456-2_14} is a variation of the \acrshort{dbscan} method. It consists
-in selecting the best clusters after testing their persistence by making the $\varepsilon$ parameter vary. It's main particularity
-is that it allows to detect clusters of different densities.
+            \acrshort{hdbscan} \cite{10.1007/978-3-642-37456-2_14} is a variation of the \acrshort{dbscan} method.
+            It consists in selecting the best clusters after testing their persistence by making the $\varepsilon$ parameter vary.
+It's main particularity is that it allows to detect clusters of different densities.
 
-To each point who belongs to a cluster is associated a probability that symbolises the degree of certainty for this point to belong
-to the said cluster.
+            To each point who belongs to a cluster is associated a probability that symbolises the degree of certainty for this point to belong to the said cluster.
 
 \section{Contributions}
-\noindent In section~\ref{sec:reminder}, we have seen that we can find the neighbours of base stations
-by combining a potential neighbouring graph and filtration criteria. This methodology gives pretty good results \cite{art_del_paq}.
+    \noindent In section~\ref{sec:reminder}, we have seen that we can find the neighbours of base stations by combining a potential neighbouring graph and filtration criteria.
+This methodology gives pretty good results \cite{art_del_paq}.
 
@@
     \subsection{Measurement of \acrshort{bs} density}
-Places with a high population also have a high density of base stations. In fact, each base station can only support a certain
-load of users.
+        Places with a high population also have a high density of base stations. In fact, each base station can only support a certain load of users.
 
-Therefore, we can assume that finding zones with a high density of base station is equivalent to finding the \acrshort{bs} 
-situated in \og cities\fg{}.
+        Therefore, we can assume that finding zones with a high density of base station is equivalent to finding the \acrshort{bs} situated in \og cities\fg{}.
 
@@
         \subsubsection{$3$-NN mean distance}
-For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in 
-$\unit{km}$). According to the value of $\gamma_i$, the base station will be classified into a different category.
+            For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in $\unit{km}$).
+According to the value of $\gamma_i$, the base station will be classified into a different category.
 
@@
         \subsubsection{Distance and angle criterion}
-As seen in section~\ref{sec:reminder}, after having found potential neighbours for each base station,
-we need to filtrate this connexions. However, this applies the same distance and angle threshold for all base stations, without taking in account the difference of density.
+            As seen in section~\ref{sec:reminder}, after having found potential neighbours for each base station, we need to filtrate this connexions.
+However, this applies the same distance and angle threshold for all base stations, without taking in account the difference of density.
 
@@
         \subsubsection{Quadrant criterion}
-This criterion has been upgraded by adding the possibility to rotate the quadrants. The offset angle selected, which is between $0$ and 
-$60$ degrees, is the one that maximises the sum of the distances of the potential neighbours to their closest quadrant delimitation.
+            This criterion has been upgraded by adding the possibility to rotate the quadrants.
+The offset angle selected, which is between $0$ and $60$ degrees, is the one that maximises the sum of the distances of the potential neighbours to their closest quadrant delimitation.
 
-In other words, it tends to select the angle with which the potential neighbors are as much in the middle of their respective quadrants
-as possible.
+            In other words, it tends to select the angle with which the potential neighbors are as much in the middle of their respective quadrants as possible.
 
@@
 \section{Conclusion}
-
     [Ouverture: prendre en compte les zazimuths]

### 2024-08-21 article.tex
Correction fautes d'autrhaurgafe

@@
 
-\title{Adaptative neigbouring methods applied to telephonic base stations}
+\title{Adaptative neighbouring methods applied to telephonic base stations}
 \author{\IEEEauthorblockN{Paul MÉHAUD}\\
@@
         When we are looking for neighbours, we need, at first, a list of potential neighbours for each point.
-        For that, we will construct a neigbouring graph $G = (P, U)$ where $P$ is the set of all points and each edge in $U$ represents a neighbouring relation.
+        For that, we will construct a neighbouring graph $G = (P, U)$ where $P$ is the set of all points and each edge in $U$ represents a neighbouring relation.
 
@@
             As introduced in a previous article \cite{10201211} its goal is to prevent all potential neighbours to be in the same angle range.
-Therefore, it was mainly thought to be used with the $k$-NN potential neigbours method.
+Therefore, it was mainly thought to be used with the $k$-NN potential neighbours method.
 
@@
                 \item \emph{$\varepsilon$}: A distance threshold under which two points are considered close enough to be considered neighbours;   
-                \item \emph{$n_{\text{min}}$}: The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.
+                \item \emph{$n_{\text{min}}$}: The shortest number of neighbours a points needs to have to be considered as a core point of a cluster.
             \end{itemize}
@@
 
-            In other words, it tends to select the angle with which the potential neighbors are as much in the middle of their respective quadrants as possible.
+            In other words, it tends to select the angle with which the potential neighbours are as much in the middle of their respective quadrants as possible.
 
@@
 \section{Results}
-
     \subsection{Measurement of \acrshort{bs} density}

### 2024-08-21 article.tex
new intro + grammar correction

@@
     Given a list of points and their coordinates, a neighbouring problem consists in finding, for each point, a list of other points that are considered as its neighbours.
+
+    The field of neighbouring problems mainly revolves around the optimisation of the $k$ nearest neighbours algorithm ($k$-NN).
+    As indicated by its name, this method consists in considering the closest $k$ points of each points as their neighbour.
+    [insert KNN reference]
+
+    Another method consists in the using the Delauney triangulation. Each couple of points linked by an edge in this triangulation are considered neighbours.
+    [insert Delauney neighbouring reference]
+
+    The default of the $k$-NN method is that it always find the same number of neighbours to each point, independantly to the reality of the geometry around each base station.
+
+    The Delaunay triangulation seems to solve this issue but it also have its own set of defaults, mostly on the borders of the data where it creates aberrant edges.
+
+    In any case, these generic methods aren't perfectly adapted to this application as real base stations are submitted to specific limitations.
+
+    Therefore, some researchs were done in order to adapt these methods to this specific application. \cite{patent_neighs}
+
+    This article aims at enhance the precision of these methods by taking into account the density of base station. It also aims at comparing the efficiency of different approaches.
+
+    Therefore, the outcome of the method presented will be a neighbouring graph where each node is a base station and each edge represent a neighbouring relationship between these two base stations.
+In [insert citation], you can see an example of neighbouring graph.
+
+    The rest of the paper is organized as follows: Section II reviews the related works relevant to our research, providing a foundation by discussing prior studies and their limitations.
+In Section III, we detail the databases used in our analysis, including data sources, update frequency, and key characteristics.
+Section IV offers a reminder on existing methods, summarizing the methodologies previously applied to similar problems and setting the stage for our proposed approach.
+Section V outlines our contributions, emphasizing the novel aspects of our work and how it advances the field.
+In Section VI, we present the results, analyzing the performance and implications of our proposed methods.
+Finally, Section VII concludes the paper, summarizing key findings and suggesting directions for future research.
 
@@
 
-            If you want this method to work properly, only \acrshort{bs} from the same provider have to be kept into the calculation process.
+            For this method to work properly, only \acrshort{bs} from the same provider have to be kept into the calculation process.
             Althought this values are working well on France, we haven't tried yet on another country.
@@
 
-            The method we propose now is to take in account those differences of density for each site to apply a different threshold according to the category the site in classified in.
+            The method we propose now is to take into account those differences of density for each site to apply a different threshold according to the category the site in classified in.
 

### 2024-08-21 article.tex
Intro finito

@@
 
-    Therefore, some researchs were done in order to adapt these methods to this specific application. \cite{patent_neighs}
+    Therefore, some researchs were done in order to adapt these methods to this specific application \cite{patent_neighs}.
 
@@
 
-    Therefore, the outcome of the method presented will be a neighbouring graph where each node is a base station and each edge represent a neighbouring relationship between these two base stations.
-In [insert citation], you can see an example of neighbouring graph.
+    Therefore, the outcome of the method presented will be a neighbouring graph, cf.
+Figure~\ref{fig:neigh_graph}, where each node is a base station and each edge represent a neighbouring relationship between these two base stations.
+    \begin{figure}
+        \centering
+        \boxed{\includegraphics[width=2.5in]{images/illus_graphs/neighbouring_graph.png}}
+        \caption{Illustration of a neighbouring graph}
+        \label{fig:neigh_graph}
+    \end{figure}
 
-    The rest of the paper is organized as follows: Section II reviews the related works relevant to our research, providing a foundation by discussing prior studies and their limitations.
-In Section III, we detail the databases used in our analysis, including data sources, update frequency, and key characteristics.
-Section IV offers a reminder on existing methods, summarizing the methodologies previously applied to similar problems and setting the stage for our proposed approach.
-Section V outlines our contributions, emphasizing the novel aspects of our work and how it advances the field.
-In Section VI, we present the results, analyzing the performance and implications of our proposed methods.
-Finally, Section VII concludes the paper, summarizing key findings and suggesting directions for future research.
+    The rest of the paper is organized as follows: Section~\ref{sec:rel_works} reviews the related works relevant to our research, providing a foundation by discussing prior studies and their limitations.
+In Section~\ref{sec:data}, we detail the databases used in our analysis, including data sources, update frequency, and key characteristics.
+Section~\ref{sec:reminder} offers a reminder on existing methods, summarizing the methodologies previously applied to similar problems and setting the stage for our proposed approach.
+Section~\ref{sec:contrib} outlines our contributions, emphasizing the novel aspects of our work and how it advances the field.
+In Section~\ref{sec:res}, we present the results, analyzing the performance and implications of our proposed methods.
+Finally, Section~\ref{sec:ccl} concludes the paper, summarizing key findings and suggesting directions for future research.
 
-\section{Related works}
+\section{Related works\label{sec:rel_works}}
     \noindent
 
-\section{Databases}
+\section{Databases\label{sec:data}}
     \noindent Several databases have been used in order to test the different aspects of the methods. However, one of them is directly necessary to the method itself.
@@
 
-\section{Contributions}
+\section{Contributions\label{sec:contrib}}
     \noindent In section~\ref{sec:reminder}, we have seen that we can find the neighbours of base stations by combining a potential neighbouring graph and filtration criteria.
@@
 
-\section{Results}
+\section{Results\label{sec:res}}
     \subsection{Measurement of \acrshort{bs} density}
@@
 
-\section{Conclusion}
+\section{Conclusion\label{sec:ccl}}
     [Ouverture: prendre en compte les zazimuths]

### 2024-08-21 article.tex
DBScan and HDBScan use explained +neighbour if covergae overlaps + 3-NN details

--- 2024-08-21 article.tex
@@
 
-    In any case, these generic methods aren't perfectly adapted to this application as real base stations are submitted to specific limitations.
+    Here we consider that two base stations are neighbours if their converage area overlap.
+Therefore, these generic methods aren't perfectly adapted to this application as these coverage areas are submitted to specific limitations like limitted radius and wave interferences.
 
@@
         \subsubsection{\acrshort{dbscan}}
-            DBScan gives only two categories : city - countryside
-            [permet de faire que 2 categories : pas assez précis (mais ptet à mettre dans résultats)]
+            The most intuitive method to use when trying to locate zones with high a high density of point is \acrshort{dbscan}.
+In fact, by applying the methods with the right parameters, these zones will each be detected in a separate cluster and the rest will be considered as noise.
+Two categories are therefore created : city (all the clusters) and countryside (the noise)
 
         \subsubsection{\acrshort{hdbscan}}
-            ...
+            We can use \acrshort{hdbscan} the same way.
+However, the previously mentionned probability associated with each point belonging to a cluster can be used to separate the center of the city (where the probability is very high) from the rest of the city.
 
@@
             For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in $\unit{km}$).
-According to the value of $\gamma_i$, the base station will be classified into a different category.
+According to the value of $\gamma_i$, the base station will be classified into a different category of density.
+In fact, a low $\gamma_i$ means that the surrounding zone is very dense in base station.
+On the contrary, a high value translate to a low density area (countryside).
 
             For this method to work properly, only \acrshort{bs} from the same provider have to be kept into the calculation process.
-            Althought this values are working well on France, we haven't tried yet on another country.
 

### 2024-08-22 article.tex
Avancement results

--- 2024-08-21 article.tex
@@
         \end{figure}
-        We can see, for example, that \emph{Free Mobile} doesn't have any base station with $2$G technology. Additionally, you can als find these values in Table~\ref{table:techno_numbers}.
+        We can see, for example, that \emph{Free Mobile} doesn't have any base station with $2$G technology. Additionally, you can also find these values in Table~\ref{table:techno_numbers}.
         \begin{table}
@@
 
+    \subsection{Best potential neighbours}
+
     \subsection{Combining criteria}
-        As a matter of optimisation, criteria are applied one after another. For example, the base graph is Delaunay triangulation and we apply distance then angle.
-        The principle is that angle criterion will be applied on the Delaunay graph filtered with the distance criterion.
+        The accuracy of the results depends on which criteria are applied to potential neighbours, and also on the order in which they are applied.
 
-        As a consequence, results differ according to the order in which the criteria are applied.
+        Firstly, we used combinations three criteria.
+When doing this experiment, we realised that the results where really convincing but, sometimes, some connexions were suppressed even if there was no reason to suppress them.
+In addition, we observed that those results were mostly influenced by when the quadrant criterion is applied.
 
-        The best is Delaunay with distance and then angle.
+        Consequently, we tried combinations of two criteria. Then, all these unexplained suppressions disappeared, especially when the quadrant criterion wasn't applied.
+
+        Now, we have to choose between angle and distance or distance and angle.
+We will keep the second option because it is more optimised.
+Indeed, the distance criterion takes less of computer ressources, thus reducing the number of operations to treat by the angle criterion.
+
+        In Figure~\ref{fig:final_neighs} you have an illustration of a portion of the results.
+To clarify, the colour of the points, which represent the base stations, is in function of the $\gamma_i$ value.
+
+        In the future, we will have a method to compare our results with a reference. [pas sûr si on garde ca]
+        \begin{figure}
+            \centering
+            \boxed{\includegraphics[width=2.5in]{images/illus_graphs/final_neighs_del_da.png}}
+            \caption{The final neighbouring graph}
+            \label{fig:final_neighs}
+        \end{figure}
 

### 2024-08-22 article.tex
Midifications mineures induites par Rob

@@
 \newacronym{anfr}{ANFR}{French National Frequency Agency}
-\newacronym{bs}{BS}{\Gls{base station}}
+\newacronym{bs}{BS}{\gls{base station}}
 \newacronym{dbscan}{DBScan}{Density-Based Spatial Clustering of Applications with Noise}
@@
 \begin{abstract}
-    The field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\% in 2023 in the world, and 97\% in France.
-Therefore, the collected datas represent a big opportunity for telecommunication companies to predict their customers behaviour for internal or marketing purposes.
-Thus, it is primordial for these companies to be able to determine if a user is moving.
-For that, it is necessary to understand the neighbouring relationships between the telephonic base stations.
-This article aims at proposing and comparing different method, that aim at adaptively detect these relationship between telephonic base stations.
-Therefore, it proposes a new method to create a neighbouring graph of base stations via their geographical positions.
+    Nowadays, it is primordial for telecommunication companies to be able to determine if a user is moving.
+For that, it is necessary to understand the neighbouring relationships between the telephonic \acrlong{bs}s.
+This article aims at proposing and comparing different method, that aim at adaptively detect these relationship between telephonic \acrlong{bs}s.
+Therefore, it proposes a new method to create a neighbouring graph of \acrlong{bs}s via their geographical positions.
 \end{abstract}
@@
 \section{Introduction}
-    \IEEEPARstart{T}{his} article articulates around the themes of mobile networks and neighbouring problems.
+    \IEEEPARstart{T}{he} field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\% in 2023 in the world, and 97\% in France.
+Therefore, the collected datas represent a big opportunity for telecommunication companies to predict their customers behaviour for internal or marketing purposes.
 
-    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known as cells, each of which is supplied by at least one fixed-location transceiver called base station.
-These base stations give the cell network coverage so that voice, data, and other kinds of content may be transmitted.
+    This article articulates around the themes of mobile networks and neighbouring problems.
+
+    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known as cells, each of which is supplied by at least one fixed-location transceiver called \acrfull{bs}.
+These \acrshort{bs}s give the cell network coverage so that voice, data, and other kinds of content may be transmitted.
 
@@
 
-    The default of the $k$-NN method is that it always find the same number of neighbours to each point, independantly to the reality of the geometry around each base station.
+    The default of the $k$-NN method is that it always find the same number of neighbours to each point, independantly to the reality of the geometry around each \acrshort{bs}.
 
@@
 
-    Here we consider that two base stations are neighbours if their converage area overlap.
+    Here two \acrshort{bs}s are considered as neighbours if their converage area overlap.
 Therefore, these generic methods aren't perfectly adapted to this application as these coverage areas are submitted to specific limitations like limitted radius and wave interferences.
@@
 
-    This article aims at enhance the precision of these methods by taking into account the density of base station. It also aims at comparing the efficiency of different approaches.
+    This article aims at enhance the precision of these methods by taking into account the density of \acrshort{bs}. It also aims at comparing the efficiency of different approaches.
 
-    Therefore, the outcome of the method presented will be a neighbouring graph, cf.
-Figure~\ref{fig:neigh_graph}, where each node is a base station and each edge represent a neighbouring relationship between these two base stations.
+    Therefore, the outcome of the method presented is a neighbouring graph, cf.
+Figure~\ref{fig:neigh_graph}, where each node is a \acrshort{bs} and each edge represent a neighbouring relationship between these two \acrshort{bs}s.
     \begin{figure}
@@
         \boxed{\includegraphics[width=2.5in]{images/illus_graphs/neighbouring_graph.png}}
-        \caption{Illustration of a neighbouring graph}
+        \caption{Illustration of a neighbouring graph.}
         \label{fig:neigh_graph}
@@
     \subsection{Main database}
-        This database \cite{main_database} contains all the information needed for the application of the method.
+        In our research we are using this database \cite{main_database} that contains all the information needed for the application of the method.
 It is from \acrfull{arcep}, which is an independent French administrative authority responsible for regulating electronic and postal communications and press distribution.
@@
         This database was first published for the third quarter of 2017 and the version we are using was published on 28\textsuperscript{th} March 2024 \cite{main_database_hist}.
-        It's updated for every quarter. For instance, the data we used refers to the fourth quarter of 2023.
+        It's updated for every quarter. For instance, this data refers to the fourth quarter of 2023.
 
@@
         Each row of the database corresponds to detailed information regarding a specific BS.
-For the scope of this study, our analysis will focus on the fields outlined in Table~\ref{table:data_columns}.
+For the scope of this study, our analysis is focusing on the fields outlined in Table~\ref{table:data_columns}.
         \begin{table}
             \centering
-            \caption{Description of the main database columns used in the experiments}
+            \caption{Description of the main database columns used in the experiments.}
             \label{table:data_columns}
@@
 
-        For station coordinates, we will use two different reference points: $x$ and $y$ coordinates, which are Lambert-93 projections of latitude and longitude.
+        For station coordinates, two different reference points are used: $x$ and $y$ coordinates, which are Lambert-93 projections of latitude and longitude.
         This dual system has two advantages: the $x$, $y$ coordinates allow us to calculate distances in meters using the Euclidean norm, which is more efficient in terms of calculation, and the GPS coordinates make it easier to display the points on a map.
 
-        In addition, we can find in the columns the name of the provider (\textsl{nom\_op}). In this database, only the four main french providers are represented:
-        \emph{Bouygues Telecom}, \emph{Free Mobile}, \emph{Orange} and \emph{SFR}.
+        In addition, in the columns the name of the provider (\textsl{nom\_op}) is given.
 
-        Finally, we have informations about the technologies used in every site. Indeed, a site can use multiple technologies.
-        In Figure~\ref{fig:data_evolution} you will find the evolution of each technology from the first updates of the data.
+        Finally, informations about the technologies used in every site is provided. Indeed, a site can use multiple technologies.
+        In Figure~\ref{fig:data_evolution} the evolution of each technology from the first updates of the data can be found.
         \begin{figure}
@@
             \boxed{\includegraphics[width=2.5in]{images/data_analysis/technos-evolution.png}}
-            \caption{Evolution by quarter year and by technology of the number of \acrshort{bs}}
+            \caption{Evolution by quarter year and by technology of the number of \acrshort{bs}.}
             \label{fig:data_evolution}
         \end{figure}
-        Then, in Figure~\ref{fig:data_technos} you will find a chart showing the number of times each technology is present for each provider.
+        Then, in Figure~\ref{fig:data_technos} a chart showing the number of times each technology is present for each provider can be found.
         \begin{figure}
@@
             \boxed{\includegraphics[width=2.5in]{images/data_analysis/with_techno.png}}
-            \caption{Breakdown, by operator, of the number of sites containing a given technology}
+            \caption{Breakdown, by operator, of the number of sites containing a given technology.}
             \label{fig:data_technos}
         \end{figure}
-        We can see, for example, that \emph{Free Mobile} doesn't have any base station with $2$G technology. Additionally, you can also find these values in Table~\ref{table:techno_numbers}.
+        We can see, for example, that \emph{Free Mobile} doesn't have any \acrshort{bs} with $2$G technology. Additionally, you can also find these values in Table~\ref{table:techno_numbers}.
         \begin{table}
             \centering
-            \caption{Number of \acrfull{bs} equipped, at least, with $x$G, by provider}
+            \caption{Number of \acrshort{bs} equipped, at least, with $x$G, by provider.}
             \label{table:techno_numbers}
@@
     \subsection{Filtering the main database}
-        As seen before this database is really huge, as a matter of fact we will only work on a portion of it.
+        As seen before this database is really big, as a matter of fact only a portion of it is used.
 
-        Firstly, only one provider will be kept because a \acrshort{bs} from provider $x$ can't be considered as a neighbour of \acrshort{bs} from provider $y$.
+        Firstly, only one provider is considered because a \acrshort{bs} from provider $x$ can't be considered as a neighbour of \acrshort{bs} from provider $y$.
         Consequently, we have chosen \emph{Orange} because it is the one that has the largest number of \acrshort{bs}.
 
-        Secondly, for the same reasons as before, only one technology is kept. Thus, we kept all \acrshort{bs} using, at least, 4G.
+        Secondly, for the same reasons as before, only one technology is considered. Thus, all \acrshort{bs} using, at least, 4G are taken into account.
 
-        In order to simplify the calculation times, the vision and the assessment of the quality of the results, we will only work on sites located in the Normandy region.
+        In order to simplify the calculation times, the vision and the assessment of the quality of the results, only sites located in the Normandy region are studied.
         This is because Normandy is where our school is based, giving us a better view of its geography.
@@
     \subsection{Additional database}
-        In order to compare the results of city detection, we needed a reference database. We therefore used the population data provided by INSEE.
+        In order to compare the results of city detection, a reference database was needed. We therefore used the population data provided by INSEE.
         [Pas sûr de l'utilité de présenter cette base en fait, ptet juste la principale suffit]
@@
     \subsection{Finding potential neighbours}
-        When we are looking for neighbours, we need, at first, a list of potential neighbours for each point.
-        For that, we will construct a neighbouring graph $G = (P, U)$ where $P$ is the set of all points and each edge in $U$ represents a neighbouring relation.
+        When looking for neighbours, at first, a list of potential neighbours for each point is necessary.
+        For that, a neighbouring graph is constructed where $P$ is the set of all points and each edge in this graph represents a neighbouring relation.
 
         \subsubsection{$k$-NN graph}
-            The most intuitive method is to connect each point to its $k$ nearest neighbours, where $k \in \mathbb{N}^*$ is a parameter to be fixed.
+            The most intuitive method is to connect each point to its $k$ nearest neighbours, where $k \in \mathbb{N}^*$ is a parameter to be set up.
 
-            However, this method can be criticised, because it always finds $k$ neighbours for each point, no matter the reality of the data.
+            However, this method can be questioned, because it always finds $k$ neighbours for each point, no matter the reality of the data.
 
@@
                 \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_Voronoi.png}}
-                \caption{Example of a Delaunay triangulation (in black) and Voronoi diagram (in red)}
+                \caption{Example of a Delaunay triangulation (in black) and Voronoi diagram (in red).}
                 \label{fig:del_tri}
@@
 
-            It consists in dividing the space around each base station into quadrants and keeping only a certain number of potential neighbours in each of the quadrants, cf. Figure~\ref{fig:crit_qua}.
+            It consists in dividing the space around each \acrshort{bs} into quadrants and keeping only a certain number of potential neighbours in each of the quadrants, cf.
+Figure~\ref{fig:crit_qua}.
             The number of quadrants has been fixed to six \cite{art_del_paq}.
@@
             \begin{itemize}
-                \item \emph{$\varepsilon$}: A distance threshold under which two points are considered close enough to be considered neighbours;   
-                \item \emph{$n_{\text{min}}$}: The shortest number of neighbours a points needs to have to be considered as a core point of a cluster.
+                \item $\varepsilon$: A distance threshold under which two points are considered close enough to be considered neighbours;   
+                \item $n_{\text{min}}$: The shortest number of neighbours a points needs to have to be considered as a core point of a cluster.
             \end{itemize}
 
-            The clusters will then \og grow\fg{} from the core points by attaching all points close from less than \emph{$\varepsilon$} than a point of the said cluster.
+            The clusters are then \og growing\fg{} from the core points by attaching all points close from less than $\varepsilon$ than a point of the said cluster.
 
@@
 \section{Contributions\label{sec:contrib}}
-    \noindent In section~\ref{sec:reminder}, we have seen that we can find the neighbours of base stations by combining a potential neighbouring graph and filtration criteria.
+    \noindent In section~\ref{sec:reminder}, we have seen that we can find the neighbours of \acrshort{bs}s by combining a potential neighbouring graph and filtration criteria.
 This methodology gives pretty good results \cite{art_del_paq}.
 
-    However, in certain cases like in a city, the filtration criteria aren't precise enough. We, therefore, need to find some ways to measure base stations' density.
+    However, in certain cases like in a city, the filtration criteria aren't precise enough. We, therefore, need to find some ways to measure \acrshort{bs}s' density.
 
     \subsection{Measurement of \acrshort{bs} density}
-        Places with a high population also have a high density of base stations. In fact, each base station can only support a certain load of users.
+        Places with a high population also have a high density of \acrshort{bs}s. In fact, each \acrshort{bs} can only support a certain load of users.
 
-        Therefore, we can assume that finding zones with a high density of base station is equivalent to finding the \acrshort{bs} situated in \og cities\fg{}.
+        Therefore, let's assume that finding zones with a high density of \acrshort{bs} is equivalent to finding the \acrshort{bs} situated in \og cities\fg{}.
 
@@
             The most intuitive method to use when trying to locate zones with high a high density of point is \acrshort{dbscan}.
-In fact, by applying the methods with the right parameters, these zones will each be detected in a separate cluster and the rest will be considered as noise.
-Two categories are therefore created : city (all the clusters) and countryside (the noise)
+In fact, by applying the methods with the right parameters, these zones are detected in separate clusters and the rest is considered as noise.
+Two categories are therefore created : city (all the clusters) and countryside (the noise).
 
@@
         \subsubsection{$3$-NN mean distance}
-            For each base station $i$, the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in $\unit{km}$).
-According to the value of $\gamma_i$, the base station will be classified into a different category of density.
-In fact, a low $\gamma_i$ means that the surrounding zone is very dense in base station.
+            For each \acrshort{bs} $p\in P$, the mean distance $\gamma_p$, in $\unit{km}$, to its three nearest neighbours is calculated.
+According to the value of $\gamma_p$, a \acrshort{bs} is classified into a different category of density.
+In fact, a low $\gamma_p$ means that the surrounding zone is very dense in \acrshort{bs}.
 On the contrary, a high value translate to a low density area (countryside).
@@
             % \begin{itemize}
-            %     \item city center: $\gamma_i\in [0,1]$;
-            %     \item urban area: $\gamma_i\in ]1,2]$;
-            %     \item extra-urban: $\gamma_i\in ]2,4]$;
-            %     \item countryside: $\gamma_i\in ]4,\infty[$.
+            %     \item city center: $\gamma_p\in [0,1]$;
+            %     \item urban area: $\gamma_p\in ]1,2]$;
+            %     \item extra-urban: $\gamma_p\in ]2,4]$;
+            %     \item countryside: $\gamma_p\in ]4,\infty[$.
             % \end{itemize}
@@
             \centering
-            \caption{Summary of criteria values}
+            \caption{Summary of criteria values.}
             \label{table:crit_summary}
@@
         \subsubsection{Distance and angle criterion}
-            As seen in section~\ref{sec:reminder}, after having found potential neighbours for each base station, we need to filtrate this connexions.
-However, this applies the same distance and angle threshold for all base stations, without taking in account the difference of density.
+            As seen in section~\ref{sec:reminder}, after having found potential neighbours for each \acrshort{bs}, this connexions needs to be filtrated.
+However, this applies the same distance and angle threshold for all \acrshort{bs}s, without taking in account the difference of density.
 
-            The method we propose now is to take into account those differences of density for each site to apply a different threshold according to the category the site in classified in.
+            The proposesd method is to take into account those differences of density for each site to apply a different threshold according to the category the site in classified in.
 
-            For both distance and angle, the more the base station is in a dense category, the lower this threshold will be.
+            For both distance and angle, the more the \acrshort{bs} is in a dense category, the lower this threshold is.
 
@@
                 \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
-                \caption{Illustation of the rotated quadrant criterion}
+                \caption{Illustation of the rotated quadrant criterion.}
                 \label{fig:crit_qua}
@@
         Now, we have to choose between angle and distance or distance and angle.
-We will keep the second option because it is more optimised.
+The second option is prefered because it is more optimised.
 Indeed, the distance criterion takes less of computer ressources, thus reducing the number of operations to treat by the angle criterion.
@@
         In Figure~\ref{fig:final_neighs} you have an illustration of a portion of the results.
-To clarify, the colour of the points, which represent the base stations, is in function of the $\gamma_i$ value.
+To clarify, the colour of the points, which represent the \acrshort{bs}s, is in function of the $\gamma_p$ value.
 
-        In the future, we will have a method to compare our results with a reference. [pas sûr si on garde ca]
+        In the future, there will be method to compare our results with a reference. [pas sûr si on garde ca]
         \begin{figure}
@@
             \boxed{\includegraphics[width=2.5in]{images/illus_graphs/final_neighs_del_da.png}}
-            \caption{The final neighbouring graph}
+            \caption{The final neighbouring graph.}
             \label{fig:final_neighs}

### 2024-08-22 article.tex
Modification taille imgs

@@
         \centering
-        \boxed{\includegraphics[width=2.5in]{images/illus_graphs/neighbouring_graph.png}}
+        \includegraphics[width=3.5in]{images/illus_graphs/neighbouring_graph.png}
         \caption{Illustration of a neighbouring graph.}
@@
             \centering
-            \boxed{\includegraphics[width=2.5in]{images/data_analysis/technos-evolution.png}}
+            \includegraphics[width=3.5in]{images/data_analysis/technos-evolution.png}
             \caption{Evolution by quarter year and by technology of the number of \acrshort{bs}.}
@@
             \centering
-            \boxed{\includegraphics[width=2.5in]{images/data_analysis/with_techno.png}}
+            \includegraphics[width=3.5in]{images/data_analysis/with_techno.png}
             \caption{Breakdown, by operator, of the number of sites containing a given technology.}
@@
                 \centering
-                \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_circumcircles_vectorial.png}}
-                \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_Voronoi.png}}
+                \includegraphics[width=1.6in]{images/illus_graphs/Delaunay_circumcircles_vectorial.png}
+                \includegraphics[width=1.6in]{images/illus_graphs/Delaunay_Voronoi.png}
                 \caption{Example of a Delaunay triangulation (in black) and Voronoi diagram (in red).}
@@
                 \centering
-                \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
+                \includegraphics[width=3.5in]{images/illus_crit/quadrant_elim.png}
                 \caption{Illustation of the rotated quadrant criterion.}
@@
             \centering
-            \boxed{\includegraphics[width=2.5in]{images/illus_graphs/final_neighs_del_da.png}}
+            \includegraphics[width=3.5in]{images/illus_graphs/final_neighs_del_da.png}
             \caption{The final neighbouring graph.}

### 2024-08-22 article.tex
abstract

--- 2024-08-22 article.tex
@@
 For that, it is necessary to understand the neighbouring relationships between the telephonic \acrlong{bs}s.
-This article aims at proposing and comparing different method, that aim at adaptively detect these relationship between telephonic \acrlong{bs}s.
-Therefore, it proposes a new method to create a neighbouring graph of \acrlong{bs}s via their geographical positions.
+This article aims at proposing and optimizing a method that adaptively detects these relationship between telephonic \acrlong{bs}s.
+This methods consists in multiple steps that can each be realised thanks to several methods that are compared : the $k$-NN method, the Delaunay triangulation or the Gabriel graph method are first used to create a first rough estimation of each point's neighbours.
+A filtering method is then applied in order to refine the neighbouring relationships that were found.
+This method is composed of several criteria that are succesfully being applied.
+These criterias are coming from previous works but were enhanced for better computational cost and results, and also to locally take into account the density of base station in the neighbours computation.
+The resulting method therefore gives a more accurate estimation of the neighbouring relationship than what was proposed before.
 \end{abstract}
-
 \section{Introduction}

### 2024-08-22 article.tex
details de grammaire

@@
 This article aims at proposing and optimizing a method that adaptively detects these relationship between telephonic \acrlong{bs}s.
+
     This methods consists in multiple steps that can each be realised thanks to several methods that are compared : the $k$-NN method, the Delaunay triangulation or the Gabriel graph method are first used to create a first rough estimation of each point's neighbours.
-A filtering method is then applied in order to refine the neighbouring relationships that were found.
-This method is composed of several criteria that are succesfully being applied.
-These criterias are coming from previous works but were enhanced for better computational cost and results, and also to locally take into account the density of base station in the neighbours computation.
+A filtering step is then applied in order to refine the neighbouring relationships that were found.
+This step is composed of several criteria that are successively being applied.
+
+    These criteria are coming from previous works but were enhanced for better computational cost and results, and also to locally take into account the density of base station in the neighbours computation.
+
     The resulting method therefore gives a more accurate estimation of the neighbouring relationship than what was proposed before.
@@
 
-    This article aims at enhance the precision of these methods by taking into account the density of \acrshort{bs}. It also aims at comparing the efficiency of different approaches.
+    This article aims at enhance the precision of these methods . It also aims at comparing the efficiency of different approaches.
 
@@
 
-    The rest of the paper is organized as follows: Section~\ref{sec:rel_works} reviews the related works relevant to our research, providing a foundation by discussing prior studies and their limitations.
-In Section~\ref{sec:data}, we detail the databases used in our analysis, including data sources, update frequency, and key characteristics.
-Section~\ref{sec:reminder} offers a reminder on existing methods, summarizing the methodologies previously applied to similar problems and setting the stage for our proposed approach.
-Section~\ref{sec:contrib} outlines our contributions, emphasizing the novel aspects of our work and how it advances the field.
+    A key finding of this article is to locally take into account the density of \acrshort{bs} in the neighbouring methodology.
+
+    The rest of the paper is organized as follows: Section~\ref{sec:rel_works} reviews the related works relevant to our research.
+In Section~\ref{sec:data}, we detail the databases used in our analysis.
+Section~\ref{sec:overview} offers a reminder on existing methods.
+Section~\ref{sec:contrib} outlines our contributions.
 In Section~\ref{sec:res}, we present the results, analyzing the performance and implications of our proposed methods.
-Finally, Section~\ref{sec:ccl} concludes the paper, summarizing key findings and suggesting directions for future research.
+Finally, Section~\ref{sec:ccl} concludes the paper and suggests directions for future research.
 
@@
     \subsection{Main database}
-        In our research we are using this database \cite{main_database} that contains all the information needed for the application of the method.
+        In this study, this database \cite{main_database} that contains all the information needed for the application of the method is being used.
 It is from \acrfull{arcep}, which is an independent French administrative authority responsible for regulating electronic and postal communications and press distribution.
 
-        This database was first published for the third quarter of 2017 and the version we are using was published on 28\textsuperscript{th} March 2024 \cite{main_database_hist}.
+        This database was first published for the third quarter of 2017 and the version used here was published on 28\textsuperscript{th} March 2024 \cite{main_database_hist}.
         It's updated for every quarter. For instance, this data refers to the fourth quarter of 2023.
@@
 
-\section{Reminder on existing methods\label{sec:reminder}}
+\section{Overview of use methods\label{sec:overview}}
     \subsection{Finding potential neighbours}

### 2024-08-22 article.tex
Res pot neigh

--- 2024-08-22 article.tex
@@
 This article aims at proposing and optimizing a method that adaptively detects these relationship between telephonic \acrlong{bs}s.
-This methods consists in multiple steps that can each be realised thanks to several methods that are compared : the $k$-NN method, the Delaunay triangulation or the Gabriel graph method are first used to create a first rough estimation of each point's neighbours.
+This methods consists in multiple steps that can each be realised thanks to several methods that are compared: the $k$-NN method, the Delaunay triangulation or the Gabriel graph method are first used to create a first rough estimation of each point's neighbours.
 A filtering method is then applied in order to refine the neighbouring relationships that were found.
@@
 In fact, by applying the methods with the right parameters, these zones are detected in separate clusters and the rest is considered as noise.
-Two categories are therefore created : city (all the clusters) and countryside (the noise).
+Two categories are therefore created: city (all the clusters) and countryside (the noise).
 
@@
     \subsection{Best potential neighbours}
+        First of all, the $k$-NN method could have provided a solution to the fact that the Delaunay triangulation does not connect all the points but makes choices.
+However, to obtain interesting connections, we need to choose a relatively high $k$, greater than 10, which implies a large number of connections and therefore an increase in   computational cost.
+What's more, applying the criteria doesn't even produce convincing results.
+
+        Secondly, the use of Gabriel's graph is not conclusive either.
+In fact, the use of this type of graph is not appropriate here because it will remove neighbourhood relationships that could have been retained.
+
+        Finally, taking into account the above conclusions, the method used to construct the potential neighbourhood is the Delaunay triangulation.
 

### 2024-08-22 article.tex

--- 2024-08-22 article.tex
@@
 
-    This methods consists in multiple steps that can each be realised thanks to several methods that are compared : the $k$-NN method, the Delaunay triangulation or the Gabriel graph method are first used to create a first rough estimation of each point's neighbours.
+    This methods consists in multiple steps that can each be realised thanks to several methods that are compared: the $k$-NN method, the Delaunay triangulation or the Gabriel graph method are first used to create a first rough estimation of each point's neighbours.
 A filtering step is then applied in order to refine the neighbouring relationships that were found.

### 2024-08-23 article.tex
Midification de typos qui etaient encore là

@@
 In Section~\ref{sec:data}, we detail the databases used in our analysis.
-Section~\ref{sec:overview} offers a reminder on existing methods.
+Section~\ref{sec:overview} offers an overview existing methods.
 Section~\ref{sec:contrib} outlines our contributions.
@@
 \section{Contributions\label{sec:contrib}}
-    \noindent In section~\ref{sec:reminder}, we have seen that we can find the neighbours of \acrshort{bs}s by combining a potential neighbouring graph and filtration criteria.
+    \noindent In section~\ref{sec:overview}, we have seen that we can find the neighbours of \acrshort{bs}s by combining a potential neighbouring graph and filtration criteria.
 This methodology gives pretty good results \cite{art_del_paq}.
@@
         \subsubsection{Distance and angle criterion}
-            As seen in section~\ref{sec:reminder}, after having found potential neighbours for each \acrshort{bs}, this connexions needs to be filtrated.
+            As seen in section~\ref{sec:overview}, after having found potential neighbours for each \acrshort{bs}, this connexions needs to be filtrated.
 However, this applies the same distance and angle threshold for all \acrshort{bs}s, without taking in account the difference of density.

### 2024-08-23 article.tex
Retrait glossaire et imports inutiles

@@
 \usepackage{amsmath,amsfonts,amssymb}
-\usepackage{algorithmic}
-\usepackage{algorithm}
+% \usepackage{algorithmic}
+% \usepackage{algorithm}
 \usepackage{array}
@@
  urlcolor=blue, linkcolor=black}
-\usepackage[acronym]{glossaries}
-\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
-
-\global\long\def\BDsites{\textsf{BD\_sites}}
 
@@
 
-\makeglossaries
-
-\setglossarypreamble{All definitions are from \href{https://www.dictionary.com/}{Dictionnary.com}}
-
-\newglossaryentry{base station}
-{
-    name=base station,
-    description={A fixed transmitter that forms part of an otherwise mobile radio network}
-}
-
-\newglossaryentry{convHull}
-{
-    name=convex hull,
-    description={The smallest convex set containing a given set}
-}
-
-\newacronym{arcep}{ARCEP}{French Regulatory Authority for Electronic Communications and Posts}
-\newacronym{anfr}{ANFR}{French National Frequency Agency}
-\newacronym{bs}{BS}{\gls{base station}}
-\newacronym{dbscan}{DBScan}{Density-Based Spatial Clustering of Applications with Noise}
-\newacronym{hdbscan}{HDBScan}{Hierarchical Density-Based Spatial Clustering of Applications with Noise}
-
 \usepackage[english,french]{babel}
@@
     Nowadays, it is primordial for telecommunication companies to be able to determine if a user is moving.
-For that, it is necessary to understand the neighbouring relationships between the telephonic \acrlong{bs}s.
-This article aims at proposing and optimizing a method that adaptively detects these relationship between telephonic \acrlong{bs}s.
+For that, it is necessary to understand the neighbouring relationships between the telephonic base stations.
+This article aims at proposing and optimizing a method that adaptively detects these relationship between telephonic base stations.
 
@@
 
-    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known as cells, each of which is supplied by at least one fixed-location transceiver called \acrfull{bs}.
-These \acrshort{bs}s give the cell network coverage so that voice, data, and other kinds of content may be transmitted.
+    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known as cells, each of which is supplied by at least one fixed-location transceiver called base station (BS).
+These BSs give the cell network coverage so that voice, data, and other kinds of content may be transmitted.
 
@@
 
-    The field of neighbouring problems mainly revolves around the optimisation of the $k$ nearest neighbours algorithm ($k$-NN).
+    The field of neighbouring problems mainly revolves around the optimisation of the $k$ Nearest Neighbours ($k$-NN) algorithm.
     As indicated by its name, this method consists in considering the closest $k$ points of each points as their neighbour.
@@
 
-    The default of the $k$-NN method is that it always find the same number of neighbours to each point, independantly to the reality of the geometry around each \acrshort{bs}.
+    The default of the $k$-NN method is that it always find the same number of neighbours to each point, independantly to the reality of the geometry around each BS.
 
@@
 
-    Here two \acrshort{bs}s are considered as neighbours if their converage area overlap.
+    Here two BSs are considered as neighbours if their converage area overlap.
 Therefore, these generic methods aren't perfectly adapted to this application as these coverage areas are submitted to specific limitations like limitted radius and wave interferences.
@@
     Therefore, the outcome of the method presented is a neighbouring graph, cf.
-Figure~\ref{fig:neigh_graph}, where each node is a \acrshort{bs} and each edge represent a neighbouring relationship between these two \acrshort{bs}s.
+Figure~\ref{fig:neigh_graph}, where each node is a BS and each edge represent a neighbouring relationship between these two BSs.
     \begin{figure}
@@
 
-    A key finding of this article is to locally take into account the density of \acrshort{bs} in the neighbouring methodology.
+    A key finding of this article is to locally take into account the density of BS in the neighbouring methodology.
 
@@
         In this study, this database \cite{main_database} that contains all the information needed for the application of the method is being used.
-It is from \acrfull{arcep}, which is an independent French administrative authority responsible for regulating electronic and postal communications and press distribution.
+It is from the French Regulatory Authority for Electronic Communications and Posts (ARCEP), which is an independent French administrative authority responsible for regulating electronic and postal communications and press distribution.
 
@@
                 \cmidrule(lr){1-2}
-                \textsl{id\_station\_anfr} & \acrshort{anfr} \acrshort{bs} ID \\ 
+                \textsl{id\_station\_anfr} & ANFR BS ID \\ 
                 \textsl{nom\_op} & Name of the provider \\
@@
                 \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
-                \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the \acrshort{bs} \\ 
+                \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the BS \\ 
                 \bottomrule
@@
             \includegraphics[width=3.5in]{images/data_analysis/technos-evolution.png}
-            \caption{Evolution by quarter year and by technology of the number of \acrshort{bs}.}
+            \caption{Evolution by quarter year and by technology of the number of BS.}
             \label{fig:data_evolution}
@@
         \end{figure}
-        We can see, for example, that \emph{Free Mobile} doesn't have any \acrshort{bs} with $2$G technology. Additionally, you can also find these values in Table~\ref{table:techno_numbers}.
+        We can see, for example, that \emph{Free Mobile} doesn't have any BS with $2$G technology. Additionally, you can also find these values in Table~\ref{table:techno_numbers}.
         \begin{table}
             \centering
-            \caption{Number of \acrshort{bs} equipped, at least, with $x$G, by provider.}
+            \caption{Number of BS equipped, at least, with $x$G, by provider.}
             \label{table:techno_numbers}
@@
 
-        Firstly, only one provider is considered because a \acrshort{bs} from provider $x$ can't be considered as a neighbour of \acrshort{bs} from provider $y$.
-        Consequently, we have chosen \emph{Orange} because it is the one that has the largest number of \acrshort{bs}.
+        Firstly, only one provider is considered because a BS from provider $x$ can't be considered as a neighbour of BS from provider $y$.
+        Consequently, we have chosen \emph{Orange} because it is the one that has the largest number of BS.
 
-        Secondly, for the same reasons as before, only one technology is considered. Thus, all \acrshort{bs} using, at least, 4G are taken into account.
+        Secondly, for the same reasons as before, only one technology is considered. Thus, all BS using, at least, 4G are taken into account.
 
@@
         \subsubsection{Delaunay triangulation}
-            A Delaunay triangulation \cite{art_delaunay} of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles do not contain any of the points.
+            A Delaunay triangulation \cite{art_delaunay} of a set of points in the plane subdivides their convex hull into triangles whose circumcircles do not contain any of the points.
 
@@
     \subsection{Finding real neighbours}
-        For the purpose of our experiments, i.e. finding \acrshort{bs} neighbours, the previously presented methods are not sufficient to find real neighbours.
+        For the purpose of our experiments, i.e. finding BS neighbours, the previously presented methods are not sufficient to find real neighbours.
         As a consequence, some neighbouring connexions needs to be suppressed \cite{patent_neighs}.
         \subsubsection{Distance criterion}
-            A \acrshort{bs} does not have an infinite coverage area.
+            A BS does not have an infinite coverage area.
             As a consequence, each edge in $U$ that is longer than a certain value, called \emph{max\_distance}, is suppressed.
@@
         \subsubsection{Angle criterion}
-            Let $p$, $q$, $r$ be three \acrshort{bs} of $P$, where $q$ and $r$ are $p$'s potential neighbours.
-As said before, coverage areas of \acrshort{bs} are limited by physics, this also implies that $r$ can be \og hidden\fg{} from $p$ by $q$ because $q$ is between $p$ and $r$ [trouver qqch pour prouver ce que je dis].
+            Let $p$, $q$, $r$ be three BS of $P$, where $q$ and $r$ are $p$'s potential neighbours.
+As said before, coverage areas of BS are limited by physics, this also implies that $r$ can be \og hidden\fg{} from $p$ by $q$ because $q$ is between $p$ and $r$ [trouver qqch pour prouver ce que je dis].
 
@@
 
-            It consists in dividing the space around each \acrshort{bs} into quadrants and keeping only a certain number of potential neighbours in each of the quadrants, cf.
-Figure~\ref{fig:crit_qua}.
+            It consists in dividing the space around each BS into quadrants and keeping only a certain number of potential neighbours in each of the quadrants, cf. Figure~\ref{fig:crit_qua}.
             The number of quadrants has been fixed to six \cite{art_del_paq}.
@@
     \subsection{Density-based clustering methods}
-        \subsubsection{\acrshort{dbscan}}
-            \acrshort{dbscan} consists in detecting clusters based on the density of points, using two parameters:
+        \subsubsection{DBScan}
+            DBScan consists in detecting clusters based on the density of points, using two parameters:
             \begin{itemize}
@@
 
-        \subsubsection{\acrshort{hdbscan}}
-            \acrshort{hdbscan} \cite{10.1007/978-3-642-37456-2_14} is a variation of the \acrshort{dbscan} method.
+        \subsubsection{HDBScan}
+            HDBScan \cite{10.1007/978-3-642-37456-2_14} is a variation of the DBScan method.
             It consists in selecting the best clusters after testing their persistence by making the $\varepsilon$ parameter vary.
@@
 \section{Contributions\label{sec:contrib}}
-    \noindent In section~\ref{sec:overview}, we have seen that we can find the neighbours of \acrshort{bs}s by combining a potential neighbouring graph and filtration criteria.
+    \noindent In section~\ref{sec:overview}, we have seen that we can find the neighbours of BSs by combining a potential neighbouring graph and filtration criteria.
 This methodology gives pretty good results \cite{art_del_paq}.
 
-    However, in certain cases like in a city, the filtration criteria aren't precise enough. We, therefore, need to find some ways to measure \acrshort{bs}s' density.
+    However, in certain cases like in a city, the filtration criteria aren't precise enough. We, therefore, need to find some ways to measure BSs' density.
 
-    \subsection{Measurement of \acrshort{bs} density}
-        Places with a high population also have a high density of \acrshort{bs}s. In fact, each \acrshort{bs} can only support a certain load of users.
+    \subsection{Measurement of BS density}
+        Places with a high population also have a high density of BSs. In fact, each BS can only support a certain load of users.
 
-        Therefore, let's assume that finding zones with a high density of \acrshort{bs} is equivalent to finding the \acrshort{bs} situated in \og cities\fg{}.
+        Therefore, let's assume that finding zones with a high density of BS is equivalent to finding the BS situated in \og cities\fg{}.
 
-        \subsubsection{\acrshort{dbscan}}
-            The most intuitive method to use when trying to locate zones with high a high density of point is \acrshort{dbscan}.
+        \subsubsection{DBScan}
+            The most intuitive method to use when trying to locate zones with high a high density of point is DBScan.
 In fact, by applying the methods with the right parameters, these zones are detected in separate clusters and the rest is considered as noise.
@@
 
-        \subsubsection{\acrshort{hdbscan}}
-            We can use \acrshort{hdbscan} the same way.
+        \subsubsection{HDBScan}
+            We can use HDBScan the same way.
 However, the previously mentionned probability associated with each point belonging to a cluster can be used to separate the center of the city (where the probability is very high) from the rest of the city.
@@
         \subsubsection{$3$-NN mean distance}
-            For each \acrshort{bs} $p\in P$, the mean distance $\gamma_p$, in $\unit{km}$, to its three nearest neighbours is calculated.
-According to the value of $\gamma_p$, a \acrshort{bs} is classified into a different category of density.
-In fact, a low $\gamma_p$ means that the surrounding zone is very dense in \acrshort{bs}.
+            For each BS $p\in P$, the mean distance $\gamma_p$, in $\unit{km}$, to its three nearest neighbours is calculated.
+According to the value of $\gamma_p$, a BS is classified into a different category of density.
+In fact, a low $\gamma_p$ means that the surrounding zone is very dense in BS.
 On the contrary, a high value translate to a low density area (countryside).
 
-            For this method to work properly, only \acrshort{bs} from the same provider have to be kept into the calculation process.
+            For this method to work properly, only BS from the same provider have to be kept into the calculation process.
 
@@
         \subsubsection{Distance and angle criterion}
-            As seen in section~\ref{sec:overview}, after having found potential neighbours for each \acrshort{bs}, this connexions needs to be filtrated.
-However, this applies the same distance and angle threshold for all \acrshort{bs}s, without taking in account the difference of density.
+            As seen in section~\ref{sec:overview}, after having found potential neighbours for each BS, this connexions needs to be filtrated.
+However, this applies the same distance and angle threshold for all BSs, without taking in account the difference of density.
 
@@
 
-            For both distance and angle, the more the \acrshort{bs} is in a dense category, the lower this threshold is.
+            For both distance and angle, the more the BS is in a dense category, the lower this threshold is.
 
@@
 \section{Results\label{sec:res}}
-    \subsection{Measurement of \acrshort{bs} density}
+    \subsection{Measurement of BS density}
 
@@
 
-        In Figure~\ref{fig:final_neighs} you have an illustration of a portion of the results.
-To clarify, the colour of the points, which represent the \acrshort{bs}s, is in function of the $\gamma_p$ value.
+        In Figure~\ref{fig:final_neighs} you have an illustration of a portion of the results. To clarify, the colour of the points, which represent the BSs, is in function of the $\gamma_p$ value.
 
@@
 
-\printglossary[type=\acronymtype]
-\printglossary
-
 \bibliographystyle{IEEEtran}

### 2024-08-23 article.tex
Retrait des we

@@
  breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=true]{hyperref}
-\hypersetup{
- urlcolor=blue, linkcolor=black}
+\hypersetup{urlcolor=blue, linkcolor=black}
 
@@
 
-        Firstly, we used combinations three criteria.
-When doing this experiment, we realised that the results where really convincing but, sometimes, some connexions were suppressed even if there was no reason to suppress them.
-In addition, we observed that those results were mostly influenced by when the quadrant criterion is applied.
+        Firstly, the tests focused on the various possible combinations of the three criteria.
+When doing this experiment, the results were really convincing but, sometimes, some connexions were suppressed even if there was no reason to suppress them.
+In addition, those results were mostly influenced by when the quadrant criterion is applied.
 
-        Consequently, we tried combinations of two criteria. Then, all these unexplained suppressions disappeared, especially when the quadrant criterion wasn't applied.
+        Consequently, combinations of two criteria were experimented. At that moment, all these unexplained suppressions disappeared, especially when the quadrant criterion wasn't applied.
 
-        Now, we have to choose between angle and distance or distance and angle.
-The second option is prefered because it is more optimised.
+        Now a choice has to be made between which criterion to apply first: distance or angle?
+The first option is prefered because it is more optimised.
 Indeed, the distance criterion takes less of computer ressources, thus reducing the number of operations to treat by the angle criterion.

### 2024-08-23 article.tex
Ajout keywords (à augmenter ptet)
finishing results

--- 2024-08-23 article.tex
@@
 
-            % \begin{itemize}
-            %     \item city center: $\gamma_p\in [0,1]$;
-            %     \item urban area: $\gamma_p\in ]1,2]$;
-            %     \item extra-urban: $\gamma_p\in ]2,4]$;
-            %     \item countryside: $\gamma_p\in ]4,\infty[$.
-            % \end{itemize}
-
     \subsection{Improvement of filtering criteria}
-        \begin{table}
-            \centering
-            \caption{Summary of criteria values.}
-            \label{table:crit_summary}
-            \begin{tabular}{lcc}
-                \toprule
-                \textbf{Description} & \textbf{\emph{max\_distance}} & \textbf{\emph{min\_angle}} \\
-                \cmidrule(lr){1-3}
-                city center & $\unit[2]{km}$ & $5^\circ$ \\
-                urban area & $\unit[5]{km}$ & $10^\circ$ \\
-                extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
-                countryside & $\unit[15]{km}$ & $20^\circ$ \\
-                \bottomrule
-            \end{tabular}
-        \end{table}
 
@@
     \subsection{Measurement of BS density}
+        Each of the three methods for detecting the high density base stations that were described above detect the major cities of France.
+It is even possible to accurately detect the name of these cities by looking, for each cluster, at the most represented "nom\_com" field of the base station of the cluster.
+
+        Morevover, the correlation coefficient between the number of inhabitant and the number of base station is above 0.9 for each of the methods.
+
+        As seen before, HDBScan is a method of variable density.
+In this use case, it is a drawback because the density of base station accurately represents the radius of each base station's coverage.
+It is therefore not advisable to treat each cluster differently.
+Plus, this method often presents aberrant clusters like the entire Corsica.
+
+        When comparing the cluster detected to the cities that have more than 7000 inhabitants, 3-NN is the method that has the best result.
+In fact, if we consider all base station with a $\gamma_p$ value inferior to 2 km to be in cities we find that the percentage at accurately classified base station is 88\%.
+It is 87\% for DBScan and 85\% for HDBScan.
+
+        Plus, as seen before, we can use the $\gamma_p$ value of the 3-NN method to classify each city in precise category, not only city vs coutryside.
+
+        Here is the classification that has been chosen : 
+        \begin{itemize}
+            \item city center: $\gamma_p\in [0,1]$;
+            \item urban area: $\gamma_p\in ]1,2]$;
+            \item extra-urban: $\gamma_p\in ]2,4]$;
+            \item countryside: $\gamma_p\in ]4,\infty[$.
+        \end{itemize}
 
@@
         Finally, taking into account the above conclusions, the method used to construct the potential neighbourhood is the Delaunay triangulation.
+
+    \subsection{Optimizing criteria parameters}
+        As seen in Section~\ref{sec:contrib}, the angle and distance criteria must adapt their threshold to the density of base station.
+The chosen thresholds for each of the previously introduced categories are presented in Table~\ref{table:crit_summary}.
+if both potential neighbours are in a different category, then the higher threshold is chosen.
+g
+        \begin{table}
+            \centering
+            \caption{Summary of criteria values.}
+            \label{table:crit_summary}
+            \begin{tabular}{lcc}
+                \toprule
+                \textbf{Description} & \textbf{\emph{max\_distance}} & \textbf{\emph{min\_angle}} \\
+                \cmidrule(lr){1-3}
+                city center & $\unit[2]{km}$ & $5^\circ$ \\
+                urban area & $\unit[5]{km}$ & $10^\circ$ \\
+                extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
+                countryside & $\unit[15]{km}$ & $20^\circ$ \\
+                \bottomrule
+            \end{tabular}
+        \end{table}
 

### 2024-08-23 article.tex

@@
 \end{abstract}
+
+\begin{IEEEkeywords}
+    Neighbours, Telecommunication, Base station, $k$-NN, Adaptative.
+\end{IEEEkeywords}
 \section{Introduction}

### 2024-08-23 article.tex
Début rel works

--- 2024-08-23 article.tex
@@
 \end{abstract}
+
+\begin{IEEEkeywords}
+    Neighbours, Telecommunication, Base station, $k$-NN, Adaptative.
+\end{IEEEkeywords}
+
 \section{Introduction}
@@
 
-    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known as cells, each of which is supplied by at least one fixed-location transceiver called base station (BS).
+    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known as cells, each of which is supplied by at least one fixed-location transceiver called Base Station (BS).
 These BSs give the cell network coverage so that voice, data, and other kinds of content may be transmitted.
@@
 
-    Another method consists in the using the Delauney triangulation. Each couple of points linked by an edge in this triangulation are considered neighbours.
-    [insert Delauney neighbouring reference]
+    Another method consists in the using the Delaunay triangulation. Each couple of points linked by an edge in this triangulation are considered neighbours.
+    [insert Delaunay neighbouring reference]
 
@@
 \section{Related works\label{sec:rel_works}}
-    \noindent
+    \noindent When looking for neighbours, the first method that comes in mind is $k$-NN.
 
@@
 \section{Contributions\label{sec:contrib}}
-    \noindent In section~\ref{sec:overview}, we have seen that we can find the neighbours of BSs by combining a potential neighbouring graph and filtration criteria.
+    \noindent In Section~\ref{sec:overview}, we have seen that we can find the neighbours of BSs by combining a potential neighbouring graph and filtration criteria.
 This methodology gives pretty good results \cite{art_del_paq}.
@@
         \subsubsection{Distance and angle criterion}
-            As seen in section~\ref{sec:overview}, after having found potential neighbours for each BS, this connexions needs to be filtrated.
+            As seen in Section~\ref{sec:overview}, after having found potential neighbours for each BS, this connexions needs to be filtrated.
 However, this applies the same distance and angle threshold for all BSs, without taking in account the difference of density.

### 2024-08-23 article.tex

--- 2024-08-23 article.tex
@@
 \end{IEEEkeywords}
+
 \section{Introduction}

### 2024-08-23 article.tex
Corrections légères de mise en page

@@
 \section{Introduction}
-    \IEEEPARstart{T}{he} field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\% in 2023 in the world, and 97\% in France.
+    \IEEEPARstart{T}{he} field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being $69\%$ in 2023 in the world, and $97\%$ in France.
 Therefore, the collected datas represent a big opportunity for telecommunication companies to predict their customers behaviour for internal or marketing purposes.
@@
         Each of the three methods for detecting the high density base stations that were described above detect the major cities of France.
-It is even possible to accurately detect the name of these cities by looking, for each cluster, at the most represented "nom\_com" field of the base station of the cluster.
+It is even possible to accurately detect the name of these cities by looking, for each cluster, at the most represented \textsl{nom\_com} field of the base station of the cluster.
 
-        Morevover, the correlation coefficient between the number of inhabitant and the number of base station is above 0.9 for each of the methods.
+        Morevover, the correlation coefficient between the number of inhabitant and the number of base station is above $0.9$ for each of the methods.
 
@@
 
-        When comparing the cluster detected to the cities that have more than 7000 inhabitants, 3-NN is the method that has the best result.
-In fact, if we consider all base station with a $\gamma_p$ value inferior to 2 km to be in cities we find that the percentage at accurately classified base station is 88\%.
-It is 87\% for DBScan and 85\% for HDBScan.
+        When comparing the cluster detected to the cities that have more than $7\,000$ inhabitants, $3$-NN is the method that has the best result.
+In fact, if we consider all base station with a $\gamma_p$ value inferior to $\unit[2]{km}$ to be in cities we find that the percentage at accurately classified base station is $88\%$.
+It is $87\%$ for DBScan and $85\%$ for HDBScan.
 
-        Plus, as seen before, we can use the $\gamma_p$ value of the 3-NN method to classify each city in precise category, not only city vs coutryside.
+        Plus, as seen before, we can use the $\gamma_p$ value of the $3$-NN method to classify each city in precise category, not only city vs coutryside.
 
-        Here is the classification that has been chosen : 
+        Here is the classification that has been chosen: 
         \begin{itemize}
@@
         First of all, the $k$-NN method could have provided a solution to the fact that the Delaunay triangulation does not connect all the points but makes choices.
-However, to obtain interesting connections, we need to choose a relatively high $k$, greater than 10, which implies a large number of connections and therefore an increase in   computational cost.
+However, to obtain interesting connections, we need to choose a relatively high $k$, greater than $10$, which implies a large number of connections and therefore an increase in   computational cost.
 What's more, applying the criteria doesn't even produce convincing results.
@@
 if both potential neighbours are in a different category, then the higher threshold is chosen.
-g
         \begin{table}
@@
 
-        In the future, there will be method to compare our results with a reference. [pas sûr si on garde ca]
+        In the future, there will be method to compare our results with a reference.
         \begin{figure}

### 2024-08-23 article.tex
Ajout des commentaires sur les img de comp

@@
 It is $87\%$ for DBScan and $85\%$ for HDBScan.
+In Figure~\ref{fig:com_3NN},~\ref{fig:com_dbs} and~\ref{fig:com_hdb} those comparisons are illustrated: in red when the reference and the method agrees on city, in green on countryside and in blue when they don't agree.
+        \begin{figure}
+            \centering
+            \includegraphics[width=3.5in]{images/city_det_comp/comp_3-NN.png}
+            \caption{City detection comparison $3$-NN.}
+            \label{fig:com_3NN}
+        \end{figure}
+        \begin{figure}
+            \centering
+            \includegraphics[width=3.5in]{images/city_det_comp/comp_dbs.png}
+            \caption{City detection comparison DBScan.}
+            \label{fig:com_dbs}
+        \end{figure}
+        \begin{figure}
+            \centering
+            \includegraphics[width=3.5in]{images/city_det_comp/comp_hdbs.png}
+            \caption{City detection comparison HDBScan.}
+            \label{fig:com_hdb}
+        \end{figure}
 

### 2024-08-23 article.tex
conclusion

--- 2024-08-23 article.tex
@@
 \end{IEEEkeywords}
-
 \section{Introduction}
@@
 
-    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known as cells, each of which is supplied by at least one fixed-location transceiver called Base Station (BS).
+    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known as cells, each of which is supplied by at least one fixed-location transceiver called base station (BS).
 These BSs give the cell network coverage so that voice, data, and other kinds of content may be transmitted.
@@
 
-    Another method consists in the using the Delaunay triangulation. Each couple of points linked by an edge in this triangulation are considered neighbours.
-    [insert Delaunay neighbouring reference]
+    Another method consists in the using the Delauney triangulation. Each couple of points linked by an edge in this triangulation are considered neighbours.
+    [insert Delauney neighbouring reference]
 
@@
 \section{Related works\label{sec:rel_works}}
-    \noindent When looking for neighbours, the first method that comes in mind is $k$-NN.
+    \noindent
 
@@
 \section{Contributions\label{sec:contrib}}
-    \noindent In Section~\ref{sec:overview}, we have seen that we can find the neighbours of BSs by combining a potential neighbouring graph and filtration criteria.
+    \noindent In section~\ref{sec:overview}, we have seen that we can find the neighbours of BSs by combining a potential neighbouring graph and filtration criteria.
 This methodology gives pretty good results \cite{art_del_paq}.
@@
         \subsubsection{Distance and angle criterion}
-            As seen in Section~\ref{sec:overview}, after having found potential neighbours for each BS, this connexions needs to be filtrated.
+            As seen in section~\ref{sec:overview}, after having found potential neighbours for each BS, this connexions needs to be filtrated.
 However, this applies the same distance and angle threshold for all BSs, without taking in account the difference of density.
@@
 
-        In the future, there will be method to compare our results with a reference. [pas sûr si on garde ca]
         \begin{figure}
@@
 \section{Conclusion\label{sec:ccl}}
-    [Ouverture: prendre en compte les zazimuths]
+    The presented method successfully detects the neighbourhood of the base stations from Orange using 4G technology in France.
+It is an upgrade from previously introduced methods because it locally takes into account the density of base station to compute the neighbouring relationships.
+
+    Future works could evaluate its performance on other providers or even, using another database, in another country.
+
+    Another important work would be to create an exact method to detect the neighbours of each base station, however the computationnal cost.
+It would allow to have an objective element of reference when tuning the parameters of the method presented here, that is the categories of $\gamma_p$ values and their associated threshold in the criterias.
+For that, it would be interesting to use a database including the azimuth angle of each base station (the direction of each antenna of the base station) to simulate the coverage of each base station and therefore be able to predict when they overlap, which means the two base stations are neighbours.
+
+    Finally, this work can be used inside bigger work that are being made in order to predict the users behaviour inside the telephonic network.
 

### 2024-08-23 article.tex

--- 2024-08-23 article.tex
@@
 
-        In the future, there will be method to compare our results with a reference.
         \begin{figure}

### 2024-08-23 article.tex
related works

--- 2024-08-23 article.tex
@@
 
-    This article aims at enhance the precision of these methods . It also aims at comparing the efficiency of different approaches.
+    This article aims at enhance the precision of these methods. It also aims at comparing the efficiency of different approaches.
 
@@
 \section{Related works\label{sec:rel_works}}
-    \noindent When looking for neighbours, the first method that comes in mind is $k$-NN.
+    \noindent When looking for neighbours, the first method that comes in mind is $k$-NN \cite{10201211}.
+
+    However, this method is not the most adapted to our specific problem. Consequently, more adapted methods can be found.
+
+    For example, the second method that is used to resolve such a problem is the Delaunay triangulation \cite{delaunay_neighbor} but this is still not perfect.
+For instance, on the border of the set of points some neighbouring connexion does not reflect the reality of physics.
+As a consequence, a method to filtrate those connexions needs to be implemented.
+
+    So, to solve this new problem, there is existing methods that can be sufficient \cite{art_del_paq, patent_neighs}, i.e. applying the same criteria for each BS.
+
+    Taking those existing methods into account, we realised that they are still not sufficient. Then, here is the major improvement of our work: take account of differences in BSs' density.
 

### 2024-09-03 article.tex
adding citations

@@
 
-    This methods consists in multiple steps that can each be realised thanks to several methods that are compared: the $k$-NN method, the Delaunay triangulation or the Gabriel graph method are first used to create a first rough estimation of each point's neighbours.
+    This methods consists in multiple steps that can each be realised thanks to several methods that are compared: the $k$-NN method, the Delaunay triangulation or the Gabriel graph method are first used to create a rough estimation of each point's neighbours.
 A filtering step is then applied in order to refine the neighbouring relationships that were found.
@@
     The field of neighbouring problems mainly revolves around the optimisation of the $k$ Nearest Neighbours ($k$-NN) algorithm.
-    As indicated by its name, this method consists in considering the closest $k$ points of each points as their neighbour.
-    [insert KNN reference]
+    As indicated by its name, this method consists in considering the closest $k$ points of each points as their neighbour \cite{art_kNN}.
 
-    Another method consists in the using the Delaunay triangulation. Each couple of points linked by an edge in this triangulation are considered neighbours.
-    [insert Delaunay neighbouring reference]
+    Another method consists in the using the Delaunay triangulation. Each couple of points linked by an edge in this triangulation are considered neighbours \cite{MULCHRONE2003689}.
 

### 2024-09-03 article.tex
Retrait des crochets

@@
         In order to compare the results of city detection, a reference database was needed. We therefore used the population data provided by INSEE.
-        [Pas sûr de l'utilité de présenter cette base en fait, ptet juste la principale suffit]
 
@@
             Let $p$, $q$, $r$ be three BS of $P$, where $q$ and $r$ are $p$'s potential neighbours.
-As said before, coverage areas of BS are limited by physics, this also implies that $r$ can be \og hidden\fg{} from $p$ by $q$ because $q$ is between $p$ and $r$ [trouver qqch pour prouver ce que je dis].
+As said before, coverage areas of BS are limited by physics, this also implies that $r$ can be \og hidden\fg{} from $p$ by $q$ because $q$ is between $p$ and $r$.
 

### 2024-09-03 article.tex
Centrage des auteurs

@@
 \title{Adaptative neighbouring methods applied to telephonic base stations}
-\author{\IEEEauthorblockN{Paul MÉHAUD}\\
-\IEEEauthorblockA{\textit{Intern at CTU in Prague} \\
-\textit{INSA Rouen Normandie}\\
-paul.mehaud@insa-rouen.fr}\\
-\and
-\IEEEauthorblockN{Brendan SÉVELLEC}\\
-\IEEEauthorblockA{\textit{Intern at CTU in Prague} \\
-\textit{INSA Rouen Normandie}\\
-brendan.sevellec@insa-rouen.fr}}
+\author{
+    \begin{tabular}{cc}
+        \IEEEauthorblockN{Paul MÉHAUD} & \IEEEauthorblockN{Brendan SÉVELLEC}\\
+        \textit{Intern at CTU in Prague} & \textit{Intern at CTU in Prague}\\
+        \textit{INSA Rouen Normandie} & \textit{INSA Rouen Normandie}\\
+        paul.mehaud@insa-rouen.fr & brendan.sevellec@insa-rouen.fr\\
+    \end{tabular}
+}
 

### 2024-09-03 article.tex
transition sentences

@@
 
-        Firstly, only one provider is considered because a BS from provider $x$ can't be considered as a neighbour of BS from provider $y$.
+        Firstly, only one provider is considered because a BS from provider A can't be considered as a neighbour of BS from provider B.
         Consequently, we have chosen \emph{Orange} because it is the one that has the largest number of BS.
@@
         When looking for neighbours, at first, a list of potential neighbours for each point is necessary.
-        For that, a neighbouring graph is constructed where $P$ is the set of all points and each edge in this graph represents a neighbouring relation.
+        For that, a neighbouring graph is constructed, where the set of nodes $P$ is composed of all the selected base stations and each edge in this graph represents a neighbouring relation.
 
         \subsubsection{$k$-NN graph}
-            The most intuitive method is to connect each point to its $k$ nearest neighbours, where $k \in \mathbb{N}^*$ is a parameter to be set up.
+            The most intuitive method to do so is to connect each point to its $k$ nearest neighbours, where $k \in \mathbb{N}^*$ is a parameter to be set up.
 
@@
     \subsection{Finding real neighbours}
-        For the purpose of our experiments, i.e. finding BS neighbours, the previously presented methods are not sufficient to find real neighbours.
-        As a consequence, some neighbouring connexions needs to be suppressed \cite{patent_neighs}.
+        For the purpose of our experiments, i.e.
+finding BS neighbours, the previously presented methods are not sufficient to find real neighbours.
+In fact, as said before, base stations are subject to physical constraints that need to be taken into account.
+
+        As a consequence, some neighbouring connexions needs to be suppressed via several criteria\cite{patent_neighs}.
         \subsubsection{Distance criterion}
@@
     \subsection{Density-based clustering methods}
+        As explained later on the paper, we need to be able to assess the density of base stations, we therefore need density based clustering methods.
         \subsubsection{DBScan}
